### 2017-06-05 ArticleDraft.Rmd
Initial Commit

---
title: "Exploring Real Data: A look at AirBnB"
author: "Amanda Francis and Eric Sullivan"
date: " "
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(dplyr)
library(pander)
library(cowplot)
library(knitr)
seattle<-read.csv('Airbnb_Seattle.csv')
currency_to_numeric <- function(x){
  # Convert currencies to numeric i.e. strip dollar signs and commas
  x <- gsub('\\$','', as.character(x))
  x <- gsub('\\,','', as.character(x))
  x <- as.numeric(x)
  return(x)
}
seattle<-seattle %>% mutate(price = currency_to_numeric(price))
```

<!--##Introduction
I THINK WE DON'T NEED THIS?  LET'S JUST JUMP RIGHT IN
… Amanda’s introduction …

… throughout this article we will propose several explorations for the reader to enjoy. …
-->

## Airbnb
We have all likely experience the traveler’s dilemma: I want to travel cheaply so that my trip can last longer, but the cost of lodging is prohibitively high.  In 2008 the San Francisco based company Airbnb changed the nature of finding lodging by creating “ … a trusted community marketplace for people to list, discover, and book unique accommodations around the world”.  In their words:  “whether an apartment for a night, a castle for a week, or a villa for a month, Airbnb connects people to unique travel experiences, at any price point, in more than 65,000 cities and 191 countries” (www.airbnb.com).

As Airbnb has grown in popularity a wealth of data has been accumulated about many aspects of the Airbnb experience. One particular independent website, insideairbnb.com, has developed “ … a set of tools and data that allows you to explore how Airbnb is really being used in cities around the world.”  Insideairbnb has gathered public data from Airbnb sites around the world and as mathematicians and statisticians this provides us with a treasure trove of questions to explore!  They have data on cities like Paris, Venice, Amsterdam, Boston, Chicago, Seattle, and many more.  Their data sets include factors such as average reviews, locations, cleaning costs, rent, and much more.

What follows are a collection of explorations that you can try out along with us.  After each exploration we’ll give some of our own thoughts,discussion, and visualization.  We encourage the reader to head over to insideairbnb.com, find some interesting data, and start exploring.

### Exploration #1: 
Go to insideairbnb.com now and find a data set for the city of your choice.  Spend a few minutes exploring the data set and propose several questions.  When you press “Get the Data” on insideairbnb.com and find your city you will see a link “see data visually here”.  Spend some time exploring their visual aids.

![](SeattlePic.png)

We are located somewhat near Seattle, so for the purposes of discussion we’ll use the Seattle data.  You are welcome to use whichever data set you find most interesting.  The graphical visualization tool allows you to see several descriptive statistics for your chosen city, animate through the frequency and location of reviews, see top rated hosts, and much more.

## Initial Exploratory Data Analysis
<!--As a way to motivate statistical thinking and exploration on these large Airbnb data sets--> Let’s explore a some questions related to your particular city (These explorations are meant to increase in difficulty as you work through them).

### Exploration #2: 
You’re trying to budget your travel money.  In what range of daily prices would you expect the average daily price for a private room at an Airbnb in a particular neighborhood to land?  **This data isn't normally distributed, so we need to be careful giving confidence intervals for single instances...**

**Discussion:** There is a beautiful beach on the Puget Sound in the Alki neighborhood of Seattle.  Let's filter the data to explore the prices from the Alki beach area.  We'll start with some basic descriptive statistics: the average rental price there is $170 but the standard deviation is $97!  The question in this exploration is really asking for a range of prices, and based on the rather large standard deviation, the estimation range will have a rather large range as well.  If this data were normally distributed we would expect *most* of the rentals (~68% of them) to be withing one standard deviation of the mean: between $73 and $267. <!--We expect the price for a rental in the Alkai neighborhood to be somewhere between $140 and $201.  In fact, a 95% confidence interval for the average price in this neighborhood is between $8 and $355!-->  The large variance in the prices leads us to believe that there is more going on here.  Let's create a data visualization to investigate further: 
```{r, echo = F,fig.height = 2,fig.width = 5}
seattle1<-seattle %>% filter(host_neighbourhood == 'Alki')
m = mean(seattle1$price)
s = sd(seattle1$price)
df<-data.frame(id = c(1,1,1,1),x = c(.5,.5,1.5,1.5), y = c(m+s, m-s, m-s, m+s))
ggplot(seattle1, aes(x = 'Alki', y = price)) + geom_violin(fill = 'cyan')+
  geom_segment(x = 0, xend = 1.5, y = m, yend = m, color = 'salmon')+
  geom_segment(aes(x = .5, xend = 1.5, y = m-s, yend = m -s ), lineend = "butt", color = 'Lightpink')+
  geom_segment(aes(x = .5, xend = 1.5, y = m+s, yend = m +s ), lineend = "butt", color = 'Lightpink') + 
  geom_boxplot(width = .4, fill = 'Lightblue')+coord_flip() + xlab('Neighborhood') + 
  ggtitle('Distribution of Prices in the Alki Neighborhood')

#ggplot(seattle1, aes(x = room_type, y = price)) + geom_violin(aes(fill = room_type)) +
#  geom_boxplot(width = .25,aes(fill = room_type ))+coord_flip()

```

<!--The most likely candidate is the type of rental (room vs. apartment vs. house).  Let’s say that we’re a bit more picky and only want a room (we’re on a budget after all).  Now after a bit more sorting and filtering the average price is only $130 but the standard deviation is even larger: $113!  Wow!  A 95% confidence interval gives a range of $45 to $220!  Well, at least we expect to find a few cheap rooms for rent.-->

The plot above is called a violin plot.  The curved shape tells us where 'clusters' of the data are located, while the boxplot tells us where the median and quartiles are located.  We observe that this data does *not* appear to be normally distributed. In fact, a relatively low concentration of the rentals in the Alki neighborhood are near the median price; many are between $40 and $80 away from the 'center', in other words, this is a bimodal distribution of data.  We could investigate the types of rentals in this data, or perhaps, their distance from the coastline to figure out what is creating this interesting shape. In addition, if we want to use prices in this neighborhood as part of some further analysis, we might consider performing some kind of variable transformation.  Since the prices here are all greater than zero, bimodal, and fairly "right skewed"", we notice that the distribution is not 'nearly normal' like we have come to expect!  A square root or log transformation might prove useful for further analysis.

### Exploration #3:  
Do you wonder if hosts with cleaner rentals charge more?  How about a more specific question:  is there a statistical difference in daily price between the rentals that are rated most cleanly versus the rentals that are rated least cleanly?

**Discussion:** <!--Since not every room in our data set has a cleanliness rating we have to do some data wrangling to remove these observations from consideration.  In doing so we realize that the sample sizes are wildly different: 81 rentals with lower cleanliness ratings and 3,166 with higher ratings.  Perhaps people are just too nice in their ratings or perhaps the Airbnb properties in Seattle are clean!-->
The first order of business in this explanation is to decide what *most cleanly* and *least cleanly* mean to us.  The cleanliness rating scale goes from 0 to 10, but we shouldn't assume that cleanliness ratings are evenly distributed among these numbers, or that the numbers 0-10 represent a nice linear progression of cleanliness.  In fact, many travelers might feel guilty giving a low cleanliness rating, so we may expect the ratings to be artificially inflated. Having learned from our last exploration, this time let's look at a visualization of the data first.  How about a scatterplot of cleanliness rating versus price?

```{r, echo = F, fig.height=2, fig.width = 5 }
seattle1<- seattle %>% 
  #filter(room_type == 'Private room') %>%
  select(review_scores_cleanliness, price)
seattle1<- seattle1 %>% filter(review_scores_cleanliness != 'N/A')

ggplot(seattle1, aes(x = review_scores_cleanliness, y = price)) + geom_point()+
  ggtitle('Scatterplot') + xlab('Cleanliness Score')
```

One problem with this graphic is that the dots we've plotted are likely hiding information from us! Some of the dots might represent only one observation, while some may have many rental observations which happen to have the same cleanliness review score and price as many others.

One option is to add a ‘jitter’ to our graphic, so that we can see all of our points (or at least get a sense about where our clusters are.

```{r, echo = F, fig.height=2.5 }
#p1<-ggplot(seattle1, aes(x = review_scores_cleanliness, y = price)) + geom_point()+
#  ggtitle('Scatterplot') + xlab('Cleanliness Score')
ggplot(seattle1, aes(x = review_scores_cleanliness, y = price)) +
  geom_jitter(shape = 1) + 
  geom_segment(y = 0, yend = 1000, x = 7.5, xend = 7.5 )+
  ggtitle('Jittered Scatterplot')+ xlab('Cleanliness Score')
#plot_grid(p1,p2,nrow=2)
```

Here we notice that the sample sizes are wildly different: 80 rentals with lower cleanliness ratings and 3,165 with higher ratings.  Perhaps people are just too nice in their ratings or perhaps the Airbnb properties in Seattle are clean! It *looks* like the rentals rated higher for cleanliness get better prices, perhaps with a few outliers. Our scatterplot dots are still so clustered that it makes it hard for us to see what's going on. Let's try one more data visualization.  In the last exploration we looked at a violin plot, and it seemed useful; this time let's look at a side-by-side violin plot. In this case, we've added a log-scale to the price variable, to make the shapes easier to see.

```{r, echo = F, fig.height = 2.5}

seattle1 <- seattle1 %>% mutate(HiLo = ifelse(review_scores_cleanliness>=8, 'High', 'Low'))

#ggplot(seattle1, aes(x = HiLo, y = price, fill = HiLo))+
#  geom_violin()+geom_boxplot( width = .4)+coord_flip()+
#  theme(legend.position = "none")+
  #scale_y_log10() + 
#  xlab('Cleanliness Rating') + ylab('Price')+ggtitle('Regular Scale')

ggplot(seattle1, aes(x = HiLo, y = price, fill = HiLo))+
  geom_violin()+geom_boxplot( width = .4)+coord_flip()+
  theme(legend.position = "none")+
  scale_y_log10() + 
  xlab('Cleanliness Rating') + ylab('Price')+ggtitle('Log Scale')

#ggplot(seattle1, aes(fill = HiLo, x = price))+stat_density()+
#  scale_x_log10() + ylab('Cleanliness Rating') + xlab('Price')+ggtitle('Distribution #of Daily Prices for High and Low Cleanliness Ratings')

```

 We see that actually, the bulk of the rental prices for *both* High and Low ratings fall below \$250, but the high rentals have some 'outlier' observations with much higher prices.  On the whole, though, the average rental in either category doesn't appear to be much different. If we conduct a statistical $t$-test on two means, we come to roughly the same conclusion (with a p-value of about 0.26), so there doesn't appear to be strong evidence of a difference in price between the two groups.  <!--At least we know that if we stay at an Airbnb rental with a higher cleanliness rating we aren’t likely being charged more.  -->

```{r, eval = F, echo = F}
# Difference of means test:

summ<-seattle1 %>% group_by(HiLo) %>% 
  summarise(m = mean(price), s = sd(price), n = n())
summ
xbardiff = summ[[1,2]] - summ[[2,2]]
stderror = sqrt(summ[[1,3]]^2/summ[[1,4]] + summ[[2,3]]^2/summ[[2,4]])
tstat = xbardiff/stderror
2*pt(-tstat,9)
```

### Exploration #4:  
I want to be safe and allow myself an out in case my travel plans fall through, but I still want to have several Airbnb rentals to choose from.  Is there a difference between the proportion of rentals in one neighborhood that have a strict cancellation policy as compared to the rentals in another neighborhood?

**Discussion:** Let’s say that we want to stay on the waterfront in Seattle so we’ll compare Alki beach and Belltown; both of which are on the water.

```{r, echo = F, fig.height=2.5}
seattle1<-seattle %>% select(cancellation_policy, host_neighbourhood)

seattle1<- seattle1 %>% filter( (host_neighbourhood == 'Alki' | 
                                      host_neighbourhood == 'Belltown'))

ggplot(seattle1, aes(x = host_neighbourhood, fill = cancellation_policy)) + 
  geom_bar(position = 'fill') + coord_flip() + ylab('Proportion')+ xlab('Neighborhood')+
  ggtitle('Cancellation Policy in Two Neighborhoods')
```

The visualization above shows us the distribution of cancellation policies in the two neighborhoods, and a statistical test on the difference of the  proportions of `strict policies` in each neighborhood gives us a p-value <!--much less than 0.001--> around .0004, and we  conclude that there is evidence to suggest that rentals in Belltown have a much stricter cancellation policy than those in Alki.  The safe bet seems to be Alki, but if we want to spend our social time in downtown we now need to consider the transportation costs.

```{r, include = F}
# Difference of proportions test:
mytable1<-seattle1 %>% filter(cancellation_policy=='strict')%>%
  group_by(host_neighbourhood) %>% tally()
mytable2<-seattle1 %>% group_by(host_neighbourhood) %>% tally()
mytable1
mytable2
p1hat= mytable1[[1,2]]/mytable2[[1,2]]
p2hat= mytable1[[2,2]]/mytable2[[2,2]]
phatdiff = p1hat - p2hat
ppooled = (mytable1[[1,2]]+mytable1[[2,2]])/(mytable2[[1,2]]+mytable2[[2,2]])
stderror = sqrt(ppooled*(1-ppooled)*(1/mytable2[[1,2]]+1/mytable2[[2,2]]))
tstat = phatdiff/stderror
2*pnorm(tstat)

# The difference between our calculations is that Eric used neighborhood_cleansed and Amanda used host_neighborhood

seattle1<-seattle %>% select(cancellation_policy, neighbourhood_cleansed)

seattle1<- seattle1 %>% filter( (neighbourhood_cleansed == 'Alki' | 
                                      neighbourhood_cleansed == 'Belltown'))

ggplot(seattle1, aes(x = neighbourhood_cleansed, fill = cancellation_policy)) + 
  geom_bar(position = 'fill') + coord_flip() + ylab('Proportion')+ xlab('Neighborhood')+
  ggtitle('Cancellation Policy in Two Neighborhoods')

mytable1<-seattle1 %>% filter(cancellation_policy=='strict')%>%
  group_by(neighbourhood_cleansed) %>% tally()
mytable2<-seattle1 %>% group_by(neighbourhood_cleansed) %>% tally()
mytable1
mytable2
p1hat= mytable1[[1,2]]/mytable2[[1,2]]
p2hat= mytable1[[2,2]]/mytable2[[2,2]]
phatdiff = p1hat - p2hat
ppooled = (mytable1[[1,2]]+mytable1[[2,2]])/(mytable2[[1,2]]+mytable2[[2,2]])
stderror = sqrt(ppooled*(1-ppooled)*(1/mytable2[[1,2]]+1/mytable2[[2,2]]))
tstat = phatdiff/stderror
2*pnorm(tstat)

#p-value = 9.214435e-05

```

### Exploration #5:

Now I'm considering inviting some friends on my trip, but first I want to know: For each additional bed,  how much more should I expect a rental to cost?

**Discussion:**
Let's start with a visualization of our data points in a (jittered) scatterplot and a contour plot showing which combinations of number of beds and rental price occur most frequently.

```{r,echo = F, fig.height = 2.5,message = F, warnings = FALSE}
seattle1<-seattle %>% select(price, beds)
seattle1<-na.omit(seattle1)
#ggpairs(airbnb6)

seattle1<-seattle1 %>%filter(beds<=14)

p1<-ggplot(seattle1, aes(x = beds, y = price)) + geom_jitter(shape = 1) + xlim(0,11)+
  #ggtitle('Price versus Number of Beds')#+ 
  geom_smooth(method = 'lm',se = F)

#p1
#ggplot(seattle1, aes(x = beds, y = price)) + 
#  stat_density2d(aes(fill = ..level..), geom="polygon")+
#  xlim(0.5,11)+ylim(0,1000)

p2<-ggplot(seattle1, aes(x = beds, y = price)) + 
  stat_density2d(na.rm=TRUE) + xlim(0.5,3.5) +ylim(0,250)
  #geom_smooth(method = 'lm')+
  #ggtitle('2D Density Contours')

plot_grid(p1, p2)
m1<-with(lm(price~beds), data = seattle1)
s<-summary(m1)
#kable(s$coefficients)

```

A simple linear regression tells us that the best-fit line for our data is approximately $Price = \$46 + 47\cdot beds$, 
so, I should expect to pay about \$93 for a rental with one bed and \$47 more per additional bed. As an additional exploration, you might try find a 95% confidence interval for the true slope (marginal price) of this regression line.  What about a 95% confidence interval for the average price of rentals with 3 beds?  What about a predicted interval for the *actual* price of a rental with 3 beds?  (How are these questions different from each other?)

<!--Do hosts that get more reviews have rentals priced differently than those with fewer reviews?

*Discussion:* To explore this question we first need to sort the data and clean out any observations that contain missing information.  This first step is called data tidying or, more loosely, data wrangling and is an important step in the data analysis process.   Next, we may want to create a data visualization to help us sense what is going on here.

```{r, include = F}
seattle1<-seattle %>% select(number_of_reviews, price) 
ggplot(seattle1, aes(x = number_of_reviews, y = price )) + geom_point() + 
  geom_smooth(method = 'lm')
m<-lm(price~number_of_reviews, data = seattle1)
pander(summary(m))

ggplot(seattle1, aes(x = number_of_reviews, y = rstandard(m) )) + geom_point() + 
  geom_smooth(method = 'lm')
pander(summary(m))

```

The question in Exploration #2 really asks to compare the mean daily prices of rentals between two distinct subgroups.  This just begs for a two-sample T test!  In the Seattle data set we find a p-value on the order of p=10-10 and hence would conclude that the two types of properties have statistically different daily prices.  But how different are they?  The actual difference between the average prices is only \$18.  Does the fact that the prices are statistically different mean that they are practically significant.  Doing a 95% confidence interval on the difference tells us that the average price for rooms with fewer than 6 reviews is likely \$13 to \$25 more expensive than the rentals with 6 or more reviews!  There might be all sorts of social reasons for this, but it looks like if you want to save the extra \$20 then you should probably rent an Airbnb that has 6 or more reviews. : -->

## Moving Beyond the Basics

In this section we pose more questions and leave the investigation open to you. If you would like to see how we answered these questions wth the Seattle data, you can visit our workfile at mathquest.carroll.edu.  Several of these exercises suggest more advanced techniques, such as multiple regression, logistic regression, or machine learning techniques to answer.

###Exploration #6:

What variables in this data set do you think would be the most useful in predicting the price of a particular rental?  Try `accommodates`, `beds`, `bathrooms`, `guests_included`, `review_scores_rating`, and various neighborhoods, <!--`QA`, `BT`, and `CH` (where `QA`, `BT` and `CH` are dummy variable for the Queen Anne,  Belltown, and Capitol Hill neighborhoods)--> and see if you can build a model (maybe a multiple regression, regression tree, or artificial neural network) that is relatively good at predicting prices. A good idea would be to split your data into a training and test sets so that you can test your predictions on data that your model has not seen.  Which variables turn out to be the most important?  The least inportant?  Does this surprise you?  Are there any variables that amount to just 'noise' in this analysis?  How reliable do you think your model is?  Do you think this same model would work in other regions of the world?  Why or why not? Do you think it would be necessary to pre-process that data in any way? For example, do you think that it would be necessary to do a principal component analysis on your data first in order to reduce the dimension of the data set?  Do you think that the variables should be transformed in any way? Do you think any additional features should be included in your data (e.g. the square of a feature, the product of two features, etc)?

<!--… multiple regression … I think we should try to predict the price of a rental unit based on the variables accommodates + beds + bathrooms +guests_included+ review_scores_rating+QA(dummy variable for Queen Anne nbd) + BTown(dummy variable for Belltown nbd)+CH(dummy variable for Capitol Hill nbd).  We try to decide which variables should count for most.  I would like to include a scatterplot matrix here. -->

### Exploration #7:

Can you use the data to predict whether a rental is an "Entire home" or a "Private room"" based on the other characteristics of that rental? 
What variables in this data set do you think would be the most useful to you?  Try using the same variables as in the last exploration (including price) to build a model? Which variables are the most important?  The least important?  Does this surprise you?  Are there any variables that amount to just 'noise' in this analysis?  How reliable do you think your model is?  **Do you think this same model would work in other regions of the world? Why or why not? Once you have a model working on your chosen city, try your model on a different city and see how it performs.**  It would also be wise in this case to split your data into a training set and a test set so that you can measure the performance of your model.

<!--… logistic regression … I think we should try to model the probability that a rental is an ‘entire house’-type rental based on either the price or the number of beds (or the # of people the rental accommodates?).  Below is an example graphic.-->

### Exploration #8:

Can you use the data to predict which neighborhood a rental is in based on other characteristics in the data?  Pick three of four neighborhoods which contain "many" rentals and keep only data from these neighborhoods.  Can you build a model (maybe hierarchical clustering, k-means, k-nearest neighbors, support vector classifiers, or something else) which can predict which neighborhood you're in, based on certain *important* variables? Which variables do you think you should use?  Do you think using `latitude` and/or `longitude` is like cheating?    How well does your model work?

##Conclusions
The Insideairbnb data set is robust enough that anyone with statistical training, no matter the sophistication, can ask meaningful and challenging questions.  In recent times the field of data science, along with the associated mathematical tools, has become a successful and popular way to analyze data sets of this type. If you want to learn morea bout exploring and using data for analysis and predictions there are starter courses on the web (e.g., Coursera and DataCamp) and many universities and colleges around the world are implementing Data Science programs.  Most importantly, as you may have found from the last three exercises, the level of mathematical sophistication associated with data analysis can be quite high, so if you are a student reading this article and you find the ideas interesting then we recommend taking courses in statistics, computer science and computational mathematics.

There are many data sets like Insiderairbnb available for free on the internet.  For example, the University of California, Irnive, hosts a collection of machine learning data sets that are at least as rich and interesting (archive.ics.uci.edu/ml/).  Ohter sites to look at when seeking include data.gov, kaggle.com, quandl.com, gapminder.org, flowingdata.com, and many others.  The world of data and data analysis is growing in importance socially and mathematicians and statisticians are uniquely positioned with their training to approach these questions with proper skills and mindsets.

### 2017-06-05 ArticleDraft.Rmd
Added code chunks to beyond the basics question

@@
 knitr::opts_chunk$set(echo = TRUE)
-library(ggplot2)
-library(dplyr)
-library(pander)
-library(cowplot)
-library(knitr)
+library(ggplot2) # graphics
+library(dplyr) # data wrangling
+library(cowplot) #plot grids
+library(knitr) # fancy tables
+library(GGally) # scatterplot matrices
+library(tree) # regression trees
+library(rpart) #classification trees
+
 seattle<-read.csv('Airbnb_Seattle.csv')
@@
 m<-lm(price~number_of_reviews, data = seattle1)
-pander(summary(m))
+#pander(summary(m))
 
@@
   geom_smooth(method = 'lm')
-pander(summary(m))
+#pander(summary(m))
 
@@
 
+```{r, echo = F, eval = F}
+seattle1<-seattle %>% select(price, accommodates, beds, bathrooms,
+                            guests_included,review_scores_rating, neighbourhood_cleansed)
+
+#What are the most popular neighbourhoods? 
+seattle1 %>% group_by(neighbourhood_cleansed) %>% tally() %>% arrange(desc(n))
+
+nbd_list<-c('Broadway', 'Wallingford', 'Belltown')
+seattle1<-seattle1 %>% filter(neighbourhood_cleansed %in% nbd_list)
+
+#Let's look at how these variables relate to each other: 
+ggpairs(seattle1, cardinality_threshold = 90)
+
+#It looks like price is correlated with accomodates, beds, and baths ... but these are also correlated with each other! Does it seem to be related to neighbourhood?
+
+seattle1 %>% group_by(neighbourhood_cleansed) %>% summarise(mean = mean(price), median = median(price))
+#Belltown seems to cost more than the other two.  Let's create a dummy variable for Belltown.
+
+seattle1<- seattle1 %>% mutate(BT=ifelse(neighbourhood_cleansed=='Belltown',1,0))
+
+#================== Use Multiple Regression =====================
+
+m1<-lm(price~ accommodates+beds+bathrooms +guests_included+review_scores_rating+BT, data = seattle1 )
+summary(m1)
+
+#At first glance it appears that we can explain about 43% of the variation in price using these variables, and the ones that seem to contribute the most are 'accomodates', 'bathrooms, 'guests_included', and 'BT' (perhaps, in that order).
+But...
+does it seem weird to you that 'beds' is not in this list?
+Can you explain why it's not?
+There are many ways to decide which variables to include (like stepwise regression, or contextual knowledge of the problem).
+Let's naively just take the ones I mentioned above:
+
+seattle2<-seattle1 %>% select(price, accommodates, bathrooms, guests_included, BT)
+seattle2<-na.omit(seattle2)
+m2<-lm(price~ accommodates+bathrooms +guests_included+BT, data = seattle2 )
+summary(m2)
+stres<-rstandard(m2)
+#Interestingly, we can now explain something like 47% of the variation in price, suggesting some of the variables we dropped were maybe acting like red herrings!
+If we choose to accept this model (which, by the way, we shouldn't -- at least not until we assess its validity!), a practical description of the model would be:
+
+#An (empty) rental costs $0. 
+# - For every person the rental accomodates, add $25.65 to the price
+# - For every bathroom in the rental, add $35.69 to the price
+# - For each guest included, add $7.27 o the rental price
+# - If the rental is in BellTown, add $19 to the price
+
+#Assess validity of model: Do the residuals appear to be normally distributed? 
+p1<-ggplot(seattle2, aes(x = accommodates, y = rstandard(m2))) + geom_point(shape = 1)
+p2<-ggplot(seattle2, aes(x = bathrooms, y = rstandard(m2))) + geom_point(shape = 1)
+p3<-ggplot(seattle2, aes(x = guests_included, y = rstandard(m2))) + geom_point(shape = 1)
+p4<-ggplot(seattle2, aes(x = lm.influence(m2)$hat, y = rstandard(m2))) + 
+  geom_point(shape = 1) + 
+  geom_vline(xintercept = 2*(5)/length(stres), color = 'cyan')+ 
+  geom_hline(yintercept = -4, color = 'red')+ 
+  geom_hline(yintercept = 4, color = 'red')
+plot_grid(p1,p2,p3,p4)
+ggplot(seattle2, aes(x = fitted(m2), y = price)) + geom_point(shape = 1)
+
+#While there is no recognizable nonlinear shape in these residual plots, we do have a number of 'outlier + leverage' points that could be skewing things for us.
+Also, the variation of residuals appears to be growing as accomodates/bathroom get larger.
+So, this model has some problems.
+
+#==================Use A Regression Tree=====================
+
+#The following code produces a regression tree for this problem:
+t<-tree(price~ accommodates+beds+bathrooms +guests_included+review_scores_rating+BT, data = seattle1 )
+t
+plot(t)
+text(t)
+
+#It appears that the most important variable in the data is 'accomodates'.  
+#If you just want to split the data into two groups, you should look to see if the renatl accomodates 8 or more people.
+If so, the average price would be $390, if not the average price would be $125.
+#For the rentals which accomodate less than 8 people, the next break occurs depending on if he rental accomodates four or more people (average price $163.10) or not (average price $102.20).
+#The next break occurs in the rentals that accommodate more than 8 people: rentals in Belltown (average price $539) or not (average price $342.70).
+
+#We can keep following the 'breaks' in this regression tree until a good 'cut-off point'.  Finding the right cut-off point is an interesting problem which you should learn more about.  
+# Further Questions: 
+#1 - Can you interpret the meaning behind all of the breaks? 
+#2 - Does the regression tree change your mind about which variables (in which cases) are practically significant? 
+#3 - Which model do you think is better?
+
+```
+
 ### Exploration #7:
@@
 
+```{r, eval = F, echo = F}
+#================== Use Multiple Logistic Regression =====================
+
+seattle1<-seattle %>% select(room_type, price, accommodates, beds, bathrooms,
+                            guests_included,review_scores_rating, neighbourhood_cleansed)
+seattle1<- seattle1 %>% filter(room_type != 'Shared room')
+seattle1<- seattle1 %>% mutate(Home = ifelse(room_type == 'Private room', 0, 1))
+
+#Which neighborhoods have more Private rentals? 
+seattle1 %>% group_by(neighbourhood_cleansed) %>% summarize(p = mean(Private))%>%
+  arrange(p)
+
+#Suppose we only use price to predict whether a rental is a private room (instead of an entire house)
+
+m1<-glm(Home~ price, family = binomial, data = seattle1 )
+c<-coefficients(m1)
+
+f<-function(x){1/(1 + exp(-c[[1]] -c[[2]]*x))}
+
+seattlebinned<-seattle1 %>% mutate(pricebin = cut(price, breaks = 20*0:100, labels = 20*0.5:99.5))
+seattleb<-seattlebinned %>% group_by(pricebin) %>% summarise(p = mean(Home))
+ggplot(seattleb, aes(x = currency_to_numeric(pricebin), y = p)) + geom_point()+
+  stat_function(fun = f, color = 'blue') + xlab('Price')+xlim(0,500)
+#The graphic deomonstrates that an increase of price is linked to an increased likelihood that the rental is an entire home.
+
+summary(m1)
+#The summary tells us that we estimate that the odds of a house being an entire home go up by .04 for every additional dollar in the price of the rental.
+
+#How well does this logistic regression do as a predictor? 
+library(mclust)
+seattle1<- seattle1 %>% mutate(Predict = ifelse(fitted(m1)>.5, 1, 0))
+classError(seattle1$Home,seattle1$Predict )
+#The classError function above tells us that our prediction gives us a 16% error rate.
+
+# Let's try adding more variables:
+
+seattle2<-na.omit(seattle1)
+m2<-glm(Home~ accommodates+beds+bathrooms +guests_included+review_scores_rating + price, family = binomial, data = seattle2 )
+summary(m2)
+
+m3<-glm(Home~ accommodates+bathrooms +review_scores_rating + price, family = binomial, data = seattle2 )
+summary(m3)
+
+seattle2<- seattle2 %>% mutate(Predict = ifelse(fitted(m3)>.5, 1, 0))
+classError(seattle2$Home,seattle2$Predict )
+#New error rate: 13%.  Not that much better?
+
+#================== Use Classification Tree =====================
+
+t<-rpart(Home~ accommodates+beds+bathrooms +guests_included+review_scores_rating + price, 
+         data = seattle2 )
+t
+plot(t, compress = TRUE)
+text(t, use.n = TRUE)
+
+#Fix plot and add interpretation
+
+```
+
 ### Exploration #8:
@@
 How well does your model work?
+
+```{r, eval = F, echo = F}
+
+seattle1<-seattle %>% select(room_type, price, accommodates, beds, bathrooms,
+                            guests_included ,review_scores_rating,
+                            neighbourhood_cleansed,latitude, longitude)
+#Which nbds should we pick
+seattle1 %>% group_by(neighbourhood_cleansed) %>% tally() %>% arrange(desc(n))
+#Howabout: 
+nbd_list<-c('Broadway', 'Belltown', 'Wallingford', 'University District', 'Minor')
+seattle1<-seattle1 %>% filter(neighbourhood_cleansed %in% nbd_list)
+ggplot(seattle1, aes(x = longitude, y = latitude, color = neighbourhood_cleansed)) + 
+  geom_point()
+
+seattle1 %>% tbl_df()
+
+clusters<-seattle1 %>%
+  mutate(Home = ifelse(room_type == 'Entire home/apt',1,0)) %>%
+  select(-neighbourhood_cleansed,-room_type)
+
+clusters<-na.omit(clusters)
+km<-kmeans(cbind(clusters[,7:8]),5)
+clusters<-clusters %>% mutate(Predict = km$cluster)
+
+ggplot(clusters, aes(x = longitude, y = latitude, color = as.factor(Predict))) + 
+  geom_point()
+
+#Still need to play around with variables.  Or, just give up and use latitude and longitude only...
+
+```
 

### 2017-06-06 ArticleDraft.Rmd
Sullivan updates to article draft 11:43am June 6

@@
 
-<!--##Introduction
-I THINK WE DON'T NEED THIS?  LET'S JUST JUMP RIGHT IN
-… Amanda’s introduction …
-
-… throughout this article we will propose several explorations for the reader to enjoy. …
--->
-
 ## Airbnb
-We have all likely experience the traveler’s dilemma: I want to travel cheaply so that my trip can last longer, but the cost of lodging is prohibitively high.
-In 2008 the San Francisco based company Airbnb changed the nature of finding lodging by creating “ … a trusted community marketplace for people to list, discover, and book unique accommodations around the world”.
+We have all likely experienced the traveler’s dilemma: I want to travel cheaply so that my trip can last longer, but the cost of lodging is prohibitively high.
+In 2008 the San Francisco based company Airbnb changed the nature of finding lodging and provided an alternative to traditional hotels by creating “ … a trusted community marketplace for people to list, discover, and book unique accommodations around the world”.
 In their words:  “whether an apartment for a night, a castle for a week, or a villa for a month, Airbnb connects people to unique travel experiences, at any price point, in more than 65,000 cities and 191 countries” (www.airbnb.com).
@@
 What follows are a collection of explorations that you can try out along with us.
-After each exploration we’ll give some of our own thoughts,discussion, and visualization.
+After each exploration we’ll give some of our own thoughts, discussion, and visualization.
 We encourage the reader to head over to insideairbnb.com, find some interesting data, and start exploring.
@@
 In what range of daily prices would you expect the average daily price for a private room at an Airbnb in a particular neighborhood to land?
-**This data isn't normally distributed, so we need to be careful giving confidence intervals for single instances...**
+<!-- **This data isn't normally distributed, so we need to be careful giving confidence intervals for single instances...** -->
 
@@
 
-**Discussion:** <!--Since not every room in our data set has a cleanliness rating we have to do some data wrangling to remove these observations from consideration.
-In doing so we realize that the sample sizes are wildly different: 81 rentals with lower cleanliness ratings and 3,166 with higher ratings.
-Perhaps people are just too nice in their ratings or perhaps the Airbnb properties in Seattle are clean!-->
-The first order of business in this explanation is to decide what *most cleanly* and *least cleanly* mean to us.
-The cleanliness rating scale goes from 0 to 10, but we shouldn't assume that cleanliness ratings are evenly distributed among these numbers, or that the numbers 0-10 represent a nice linear progression of cleanliness.
+**Discussion:** 
+The first order of business in this exploration is to decide what *most cleanly* and *least cleanly* mean to us.
+The cleanliness rating scale goes from 0 to 10, but we shouldn't assume that cleanliness ratings are evenly distributed among these numbers, or that the numbers 0-10 represent a linear progression of cleanliness.
 In fact, many travelers might feel guilty giving a low cleanliness rating, so we may expect the ratings to be artificially inflated.
@@
   scale_y_log10() + 
-  xlab('Cleanliness Rating') + ylab('Price')+ggtitle('Log Scale')
+  xlab('Cleanliness Rating') + ylab('Price')+ggtitle('Price on a Log Scale')
 
@@
 
-The visualization above shows us the distribution of cancellation policies in the two neighborhoods, and a statistical test on the difference of the  proportions of `strict policies` in each neighborhood gives us a p-value <!--much less than 0.001--> around .0004, and we  conclude that there is evidence to suggest that rentals in Belltown have a much stricter cancellation policy than those in Alki.
+The visualization above shows us the distribution of cancellation policies in the two neighborhoods, and a statistical test on the difference of the  proportions of `strict policies` in each neighborhood gives us a p-value around .0004, and we  conclude that there is evidence to suggest that rentals in Belltown have a much stricter cancellation policy than those in Alki.
 The safe bet seems to be Alki, but if we want to spend our social time in downtown we now need to consider the transportation costs.
@@
 2*pnorm(tstat)
-
-# The difference between our calculations is that Eric used neighborhood_cleansed and Amanda used host_neighborhood
 
@@
 tstat = phatdiff/stderror
-2*pnorm(tstat)
+pvalue = 2*pnorm(tstat)
 
@@
 ### Exploration #5:
-
 Now I'm considering inviting some friends on my trip, but first I want to know: For each additional bed,  how much more should I expect a rental to cost?
@@
 ## Moving Beyond the Basics 
-
-In this section we pose more questions and leave the investigation open to you.
-If you would like to see how we answered these questions wth the Seattle data, you can visit our workfile at mathquest.carroll.edu.
+In this section we pose more questions and leave the investigations open to you.
+If you would like to see how we answered these questions wth the Seattle data, you can visit our workfile at mathquest.carroll.edu/AirbnbExplorations/.
 Several of these exercises suggest more advanced techniques, such as multiple regression, logistic regression, or machine learning techniques to answer.
@@
 ###Exploration #6: 
-
 What variables in this data set do you think would be the most useful in predicting the price of a particular rental?
-Try `accommodates`, `beds`, `bathrooms`, `guests_included`, `review_scores_rating`, and various neighborhoods, <!--`QA`, `BT`, and `CH` (where `QA`, `BT` and `CH` are dummy variable for the Queen Anne,  Belltown, and Capitol Hill neighborhoods)--> and see if you can build a model (maybe a multiple regression, regression tree, or artificial neural network) that is relatively good at predicting prices.
+Try `accommodates`, `beds`, `bathrooms`, `guests_included`, `review_scores_rating`, and various neighborhoods, and see if you can build a model (maybe a multiple regression, regression tree, or artificial neural network) that is *good* at predicting prices.
 A good idea would be to split your data into a training and test sets so that you can test your predictions on data that your model has not seen.
@@
 Do you think it would be necessary to pre-process that data in any way?
-For example, do you think that it would be necessary to do a principal component analysis on your data first in order to reduce the dimension of the data set?
-Do you think that the variables should be transformed in any way?
+<!--For example, do you think that it would be necessary to do a principal component analysis on your data first in order to reduce the dimension of the data set?-->  Do you think that the variables should be transformed in any way?
 Do you think any additional features should be included in your data (e.g.
@@
 plot(t)
-text(t)
+text(t) # *********** this line errors **************
 
@@
 ### Exploration #7: 
-
 Can you use the data to predict whether a rental is an "Entire home" or a "Private room"" based on the other characteristics of that rental? 
@@
 ### Exploration #8: 
-
 Can you use the data to predict which neighborhood a rental is in based on other characteristics in the data?
-Pick three of four neighborhoods which contain "many" rentals and keep only data from these neighborhoods.
-Can you build a model (maybe hierarchical clustering, k-means, k-nearest neighbors, support vector classifiers, or something else) which can predict which neighborhood you're in, based on certain *important* variables?
+Pick three or four neighborhoods which contain "many" rentals and keep only data from these neighborhoods.
+Can you build a model (maybe hierarchical clustering, k-nearest neighbors, support vector classifiers, or something else) which can predict which neighborhood you're in, based on certain *important* variables?
 Which variables do you think you should use?
@@
 In recent times the field of data science, along with the associated mathematical tools, has become a successful and popular way to analyze data sets of this type.
-If you want to learn morea bout exploring and using data for analysis and predictions there are starter courses on the web (e.g., Coursera and DataCamp) and many universities and colleges around the world are implementing Data Science programs.
+If you want to learn more about exploring and using data for analysis and predictions there are starter courses on the web (e.g., Coursera and DataCamp) and many universities and colleges around the world are implementing Data Science programs.
 Most importantly, as you may have found from the last three exercises, the level of mathematical sophistication associated with data analysis can be quite high, so if you are a student reading this article and you find the ideas interesting then we recommend taking courses in statistics, computer science and computational mathematics.
@@
 For example, the University of California, Irnive, hosts a collection of machine learning data sets that are at least as rich and interesting (archive.ics.uci.edu/ml/).
-Ohter sites to look at when seeking include data.gov, kaggle.com, quandl.com, gapminder.org, flowingdata.com, and many others.
+Other sites to look at when seeking data sets include data.gov, kaggle.com, quandl.com, gapminder.org, flowingdata.com, and many others.
 The world of data and data analysis is growing in importance socially and mathematicians and statisticians are uniquely positioned with their training to approach these questions with proper skills and mindsets.

### 2017-06-06 ArticleDraft.Rmd
Test Commit

@@
 Pick three or four neighborhoods which contain "many" rentals and keep only data from these neighborhoods.
-Can you build a model (maybe hierarchical clustering, k-nearest neighbors, support vector classifiers, or something else) which can predict which neighborhood you're in, based on certain *important* variables?
+Can you build a model (maybe hierarchical clustering, k-means, or something else) which can predict which neighborhood you're in, based on certain *important* variables?
 Which variables do you think you should use?
@@
 clusters<-na.omit(clusters)
-km<-kmeans(cbind(clusters[,7:8]),5)
+km<-kmeans(cbind(clusters[,1:8]),5)
 clusters<-clusters %>% mutate(Predict = km$cluster)

### 2017-06-06 ArticleDraft.Rmd
Sullivan edits 2:01pm June 6

@@
 Several of these exercises suggest more advanced techniques, such as multiple regression, logistic regression, or machine learning techniques to answer.
-
-###Exploration #6: 
-What variables in this data set do you think would be the most useful in predicting the price of a particular rental?
-Try `accommodates`, `beds`, `bathrooms`, `guests_included`, `review_scores_rating`, and various neighborhoods, and see if you can build a model (maybe a multiple regression, regression tree, or artificial neural network) that is *good* at predicting prices.
-A good idea would be to split your data into a training and test sets so that you can test your predictions on data that your model has not seen.
-Which variables turn out to be the most important?
+A good idea for each of the following explorations would be to split your data into a training and a test set so that you can test your predictions on data that your model has not seen.
+As you work on these explorations consider the following questions: Which variables turn out to be the most important?
 The least inportant?
-Does this surprise you?
 Are there any variables that amount to just 'noise' in this analysis?
@@
 the square of a feature, the product of two features, etc)?
+
+###Exploration #6: 
+What variables in this data set do you think would be the most useful in predicting the price of a particular rental?
+Try `accommodates`, `beds`, `bathrooms`, `guests_included`, `review_scores_rating`, and various neighborhoods, and see if you can build a model (maybe a multiple regression, regression tree, or artificial neural network) that is *good* at predicting prices.
 
@@
 Can you use the data to predict whether a rental is an "Entire home" or a "Private room"" based on the other characteristics of that rental? 
-What variables in this data set do you think would be the most useful to you?
-Try using the same variables as in the last exploration (including price) to build a model?
-Which variables are the most important?
+What variables in this data set do you think would be the most useful to you?  Try using the same variables as in the last exploration (including price) to build a model? 
+<!--Which variables are the most important?
 The least important?
@@
 Once you have a model working on your chosen city, try your model on a different city and see how it performs.**  It would also be wise in this case to split your data into a training set and a test set so that you can measure the performance of your model.
+-->
 
@@
 The Insideairbnb data set is robust enough that anyone with statistical training, no matter the sophistication, can ask meaningful and challenging questions.
-In recent times the field of data science, along with the associated mathematical tools, has become a successful and popular way to analyze data sets of this type.
+In recent times the field of data science has become a successful and popular way to analyze data sets of this type.
 If you want to learn more about exploring and using data for analysis and predictions there are starter courses on the web (e.g., Coursera and DataCamp) and many universities and colleges around the world are implementing Data Science programs.

### 2017-06-06 ArticleDraft.Rmd
Mathmanda edits up to Beyond the Basics

@@
 seattle<-seattle %>% mutate(price = currency_to_numeric(price))
+showcode<-F
 ```
+
+Data is seemingly everywhere these days, and is becoming more powerful as we learn how to use it to answer important questions.
+In this article we highlight one freely-available, rich and complex data set which you might use to try out asking and answering data-driven questions.
+
+What follows are a collection of explorations that you can try out along with us.
+After each exploration we’ll give some of our own thoughts, discussion, and visualization.
+We encourage the reader to head over to insideairbnb.com, find some interesting data, and start exploring.
 
@@
 
-As Airbnb has grown in popularity a wealth of data has been accumulated about many aspects of the Airbnb experience.
-One particular independent website, insideairbnb.com, has developed “ … a set of tools and data that allows you to explore how Airbnb is really being used in cities around the world.”  Insideairbnb has gathered public data from Airbnb sites around the world and as mathematicians and statisticians this provides us with a treasure trove of questions to explore!
-They have data on cities like Paris, Venice, Amsterdam, Boston, Chicago, Seattle, and many more.
+As Airbnb has grown in popularity, a wealth of data has been accumulated about many aspects of the Airbnb experience.
+One particular independent website, insideairbnb.com, has developed “ … a set of tools and data that allows you to explore how Airbnb is really being used in cities around the world.”  Insideairbnb has gathered public data from Airbnb sites around the world and <!--as mathematicians and statisticians--> this provides us with a treasure trove of questions to explore!
+<!--They have data on cities like Paris, Venice, Amsterdam, Boston, Chicago, Seattle, and many more.
 Their data sets include factors such as average reviews, locations, cleaning costs, rent, and much more.
-
-What follows are a collection of explorations that you can try out along with us.
-After each exploration we’ll give some of our own thoughts, discussion, and visualization.
-We encourage the reader to head over to insideairbnb.com, find some interesting data, and start exploring.
+-->
 
@@
 
-We are located somewhat near Seattle, so for the purposes of discussion we’ll use the Seattle data.
+We are located somewhat near Seattle, so, for our discussions, we’ll use the Seattle data.
 You are welcome to use whichever data set you find most interesting.
@@
 ## Initial Exploratory Data Analysis
-<!--As a way to motivate statistical thinking and exploration on these large Airbnb data sets--> Let’s explore a some questions related to your particular city (These explorations are meant to increase in difficulty as you work through them).
+<!--As a way to motivate statistical thinking and exploration on these large Airbnb data sets--> Let’s explore some questions related to your particular city (These explorations are meant to increase in difficulty as you work through them).
 
@@
 You’re trying to budget your travel money.
-In what range of daily prices would you expect the average daily price for a private room at an Airbnb in a particular neighborhood to land?
-<!-- **This data isn't normally distributed, so we need to be careful giving confidence intervals for single instances...** -->
+Give a *pracical* estimate for the daily prices of an Airbnb rentals in a particular neighborhood.
+<!-- In what range of daily prices would you expect the average daily price for a private room at an Airbnb in a particular neighborhood to land?
+**This data isn't normally distributed, so we need to be careful giving confidence intervals for single instances...** -->
 
 **Discussion:** There is a beautiful beach on the Puget Sound in the Alki neighborhood of Seattle.
-Let's filter the data to explore the prices from the Alki beach area.
-We'll start with some basic descriptive statistics: the average rental price there is $170 but the standard deviation is $97!
-The question in this exploration is really asking for a range of prices, and based on the rather large standard deviation, the estimation range will have a rather large range as well.
-If this data were normally distributed we would expect *most* of the rentals (~68% of them) to be withing one standard deviation of the mean: between $73 and $267.
+Let's filter the data to explore the prices of rentals from the Alki beach area.
+We'll start with some basic descriptive statistics: the average rental price there is $172 but the standard deviation is $97!
+The question in this exploration is best answered with a range of prices, and, based on the rather large standard deviation, the estimate will have a rather large range as well.
+If this data were normally distributed we would expect *most* of the rentals (~68% of them) to be withing one standard deviation of the mean: between $75 and $269.
 <!--We expect the price for a rental in the Alkai neighborhood to be somewhere between $140 and $201.
@@
 Let's create a data visualization to investigate further:
-```{r, echo = F,fig.height = 2,fig.width = 5}
-seattle1<-seattle %>% filter(host_neighbourhood == 'Alki')
+
+```{r, echo = showcode,fig.height = 2,fig.width = 5}
+#First we filter our data so that only includes the neighbourhood we care about: 
+seattle1<-seattle %>% filter(neighbourhood_cleansed == 'Alki')
+
+#Calculate the mean and standard deviation:
 m = mean(seattle1$price)
 s = sd(seattle1$price)
-df<-data.frame(id = c(1,1,1,1),x = c(.5,.5,1.5,1.5), y = c(m+s, m-s, m-s, m+s))
+
+#Create a boxplot + violin plot to see what prices happen most: 
 ggplot(seattle1, aes(x = 'Alki', y = price)) + geom_violin(fill = 'cyan')+
-  geom_segment(x = 0, xend = 1.5, y = m, yend = m, color = 'salmon')+
-  geom_segment(aes(x = .5, xend = 1.5, y = m-s, yend = m -s ), lineend = "butt", color = 'Lightpink')+
-  geom_segment(aes(x = .5, xend = 1.5, y = m+s, yend = m +s ), lineend = "butt", color = 'Lightpink') + 
-  geom_boxplot(width = .4, fill = 'Lightblue')+coord_flip() + xlab('Neighborhood') + 
+  geom_boxplot(width = .3, fill = 'Lightblue')+coord_flip() + xlab('') + ylab('Price')+
   ggtitle('Distribution of Prices in the Alki Neighborhood')
-
-#ggplot(seattle1, aes(x = room_type, y = price)) + geom_violin(aes(fill = room_type)) +
-#  geom_boxplot(width = .25,aes(fill = room_type ))+coord_flip()
-
 ```
@@
 The plot above is called a violin plot.
-The curved shape tells us where 'clusters' of the data are located, while the boxplot tells us where the median and quartiles are located.
+The curved shape tells us where 'clusters' of the data are located, while the boxplot tells us where the median and quartiles are.
 We observe that this data does *not* appear to be normally distributed.
-In fact, a relatively low concentration of the rentals in the Alki neighborhood are near the median price; many are between $40 and $80 away from the 'center', in other words, this is a bimodal distribution of data.
-We could investigate the types of rentals in this data, or perhaps, their distance from the coastline to figure out what is creating this interesting shape.
-In addition, if we want to use prices in this neighborhood as part of some further analysis, we might consider performing some kind of variable transformation.
-Since the prices here are all greater than zero, bimodal, and fairly "right skewed"", we notice that the distribution is not 'nearly normal' like we have come to expect!
-A square root or log transformation might prove useful for further analysis.
+In fact, a relatively low concentration of the rentals in the Alki neighborhood are near the mean price; many are between $40 and $100 away from the 'center'.
+You may want to investigate the types of rentals in this data, or perhaps, their distance from the coastline to figure out what is creating this interesting shape.
+In addition, if we want to use prices in this neighborhood as part of some further analysis, we might consider performing a variable transformation.
+Since the prices here are all greater than zero, bimodal, and fairly "right skewed" a square root or log transformation might prove useful for further analysis.
 
@@
 Do you wonder if hosts with cleaner rentals charge more?
-How about a more specific question:  is there a statistical difference in daily price between the rentals that are rated most cleanly versus the rentals that are rated least cleanly?
+Here is a more specific question:  is there a significant difference between the daily price of the *cleanest* rentals verus the *least clean* rentals?
 
 **Discussion:** 
-The first order of business in this exploration is to decide what *most cleanly* and *least cleanly* mean to us.
-The cleanliness rating scale goes from 0 to 10, but we shouldn't assume that cleanliness ratings are evenly distributed among these numbers, or that the numbers 0-10 represent a linear progression of cleanliness.
+The first order of business in this exploration is to decide what *cleanest and *least clean* mean to us.
+The cleanliness rating scale goes from 0 to 10, but we shouldn't assume that cleanliness ratings are evenly distributed among these numbers, or even that the numbers 0-10 represent a linear progression of cleanliness.
 In fact, many travelers might feel guilty giving a low cleanliness rating, so we may expect the ratings to be artificially inflated.
@@
 
-```{r, echo = F, fig.height=2, fig.width = 5 }
+```{r, echo = showcode, fig.height=2, fig.width = 5 }
+#For simplicity, let's eliminate all variables except cleanliness score and price
+# and eliminate any missing data
+# .... though .... we should consider what missing data might mean about a rental ...
 seattle1<- seattle %>% 
-  #filter(room_type == 'Private room') %>%
-  select(review_scores_cleanliness, price)
-seattle1<- seattle1 %>% filter(review_scores_cleanliness != 'N/A')
+  select(review_scores_cleanliness, price)%>%
+  filter(review_scores_cleanliness != 'N/A')
 
+#Make a scatterplot of cleanliness rating versus price: 
 ggplot(seattle1, aes(x = review_scores_cleanliness, y = price)) + geom_point()+
-  ggtitle('Scatterplot') + xlab('Cleanliness Score')
+  ggtitle('Scatterplot') + xlab('Cleanliness Score') + ylab('Price')
 ```
 
-One problem with this graphic is that the dots we've plotted are likely hiding information from us!
-Some of the dots might represent only one observation, while some may have many rental observations which happen to have the same cleanliness review score and price as many others.
+One problem with this graphic is that the dots we've plotted are likely hiding the very information we want!
+<!--Some of the dots might represent only one observation, while some may have many rental observations which happen to have the same cleanliness review score and price as many others.
+--> We assume that every dot we see represents one rental, but there may be places in this scatterplot where many dots all landed on top of each other.
 
-One option is to add a ‘jitter’ to our graphic, so that we can see all of our points (or at least get a sense about where our clusters are.
+One option is to add a ‘jitter’ to our graphic, so that we can see all (or, at least, more) of our points, which will help us get a sense about where our clusters are.
 
-```{r, echo = F, fig.height=2.5 }
-#p1<-ggplot(seattle1, aes(x = review_scores_cleanliness, y = price)) + geom_point()+
-#  ggtitle('Scatterplot') + xlab('Cleanliness Score')
+```{r, echo = showcode, fig.height=2.5 }
+# We make a jittered scatterplot, and indicate a potential cut-off value for 
+# cleanest vs least clean: 
 ggplot(seattle1, aes(x = review_scores_cleanliness, y = price)) +
   geom_jitter(shape = 1) + 
-  geom_segment(y = 0, yend = 1000, x = 7.5, xend = 7.5 )+
-  ggtitle('Jittered Scatterplot')+ xlab('Cleanliness Score')
-#plot_grid(p1,p2,nrow=2)
+  geom_segment(y = 0, yend = 1000, x = 7.5, xend = 7.5 , color = 'red')+
+  ggtitle('Jittered Scatterplot')+ xlab('Cleanliness Score')+ ylab('Price')
 ```
 
-Here we notice that the sample sizes are wildly different: 80 rentals with lower cleanliness ratings and 3,165 with higher ratings.
-Perhaps people are just too nice in their ratings or perhaps the Airbnb properties in Seattle are clean!
-It *looks* like the rentals rated higher for cleanliness get better prices, perhaps with a few outliers.
-Our scatterplot dots are still so clustered that it makes it hard for us to see what's going on.
-Let's try one more data visualization.
-In the last exploration we looked at a violin plot, and it seemed useful; this time let's look at a side-by-side violin plot.
+The jittered scatterplot suggests that 7 might be a good *cut-off* value for separating clean and unclean rentals.
+Notice that the sample sizes are wildly different: 80 rentals with lower cleanliness ratings and 3,165 with higher ratings.
+<!--Perhaps people are just too nice in their ratings or perhaps the Airbnb properties in Seattle are clean!--> It *looks* like the rentals rated higher for cleanliness get better prices, perhaps with a few outliers.
+However, our scatterplot dots are still so clustered that it makes it hard for us to see what's going on.
+Let's try <!--one more data visualization.
+In the last exploration we looked at a violin plot, and it seemed useful; this time let's look at--> a side-by-side violin plot.
 In this case, we've added a log-scale to the price variable, to make the shapes easier to see.
 
-```{r, echo = F, fig.height = 2.5}
-
+```{r, echo = showcode, fig.height = 2.5}
+#Let's create a new variable that separates the clean from the unclean!
 seattle1 <- seattle1 %>% mutate(HiLo = ifelse(review_scores_cleanliness>=8, 'High', 'Low'))
 
-#ggplot(seattle1, aes(x = HiLo, y = price, fill = HiLo))+
-#  geom_violin()+geom_boxplot( width = .4)+coord_flip()+
-#  theme(legend.position = "none")+
-  #scale_y_log10() + 
-#  xlab('Cleanliness Rating') + ylab('Price')+ggtitle('Regular Scale')
-
+#Now we make side by side violin and boxplots, so we can compare prices 
+#of the two groups: 
 ggplot(seattle1, aes(x = HiLo, y = price, fill = HiLo))+
@@
   xlab('Cleanliness Rating') + ylab('Price')+ggtitle('Price on a Log Scale')
-
-#ggplot(seattle1, aes(fill = HiLo, x = price))+stat_density()+
-#  scale_x_log10() + ylab('Cleanliness Rating') + xlab('Price')+ggtitle('Distribution #of Daily Prices for High and Low Cleanliness Ratings')
-
 ```
 
- We see that actually, the bulk of the rental prices for *both* High and Low ratings fall below \$250, but the high rentals have some 'outlier' observations with much higher prices.
-On the whole, though, the average rental in either category doesn't appear to be much different.
-If we conduct a statistical $t$-test on two means, we come to roughly the same conclusion (with a p-value of about 0.26), so there doesn't appear to be strong evidence of a difference in price between the two groups.
+ We see that actually, the bulk of the rental prices for *both* High and Low ratings are centered near $100, but the high rentals have some 'outlier' observations with much higher prices.
+On the whole, though, the average rental price in either category doesn't appear to be drastically different.
+If we conduct a statistical $t$-test on two means, we come to roughly the same conclusion (with a p-value of about 0.23), so there doesn't appear to be strong evidence of a difference in price between the two groups.
 <!--At least we know that if we stay at an Airbnb rental with a higher cleanliness rating we aren’t likely being charged more.
@@
 
-```{r, eval = F, echo = F}
-# Difference of means test:
-
+```{r, eval = F, echo = showcode}
+#Let's look at a few descriptive statistics for our data: 
 summ<-seattle1 %>% group_by(HiLo) %>% 
@@
 summ
-xbardiff = summ[[1,2]] - summ[[2,2]]
-stderror = sqrt(summ[[1,3]]^2/summ[[1,4]] + summ[[2,3]]^2/summ[[2,4]])
-tstat = xbardiff/stderror
-2*pt(-tstat,9)
+
+# Difference of means test:
+Clean<- seattle1 %>% filter(HiLo =='High')
+Unclean<- seattle1 %>% filter(HiLo =='Low')
+test<-t.test(Clean$price, Unclean$price)
+test
 ```
@@
 
-**Discussion:** Let’s say that we want to stay on the waterfront in Seattle so we’ll compare Alki beach and Belltown; both of which are on the water.
+**Discussion:** Let’s say that we want to stay on the waterfront in Seattle so we’ll compare Alki beach and Belltown, both of which are on the water.
 
-```{r, echo = F, fig.height=2.5}
-seattle1<-seattle %>% select(cancellation_policy, host_neighbourhood)
+```{r, echo = showcode, fig.height=2.5}
+#Let's eliminate all variables except neighbourhood and cancellation policies,
+# and filter out the irrelevant neighbourhoods.
+seattle1<-seattle %>%
+  select(cancellation_policy,neighbourhood_cleansed)%>%
+  filter( (neighbourhood_cleansed == 'Alki' |  neighbourhood_cleansed == 'Belltown'))
 
-seattle1<- seattle1 %>% filter( (host_neighbourhood == 'Alki' | 
-                                      host_neighbourhood == 'Belltown'))
-
-ggplot(seattle1, aes(x = host_neighbourhood, fill = cancellation_policy)) + 
+#Create a visualization showing the different distributions of cancellation policies
+ggplot(seattle1, aes(x = neighbourhood_cleansed, fill = cancellation_policy)) + 
   geom_bar(position = 'fill') + coord_flip() + ylab('Proportion')+ xlab('Neighborhood')+
@@
 
-The visualization above shows us the distribution of cancellation policies in the two neighborhoods, and a statistical test on the difference of the  proportions of `strict policies` in each neighborhood gives us a p-value around .0004, and we  conclude that there is evidence to suggest that rentals in Belltown have a much stricter cancellation policy than those in Alki.
+The visualization above shows us the distribution of cancellation policies in the two neighborhoods, and a statistical test on the difference of the  proportions of *strict* policies in each neighborhood gives us a p-value much less than .01, and we  conclude that there is evidence to suggest that rentals in Belltown have a much stricter cancellation policy than those in Alki.
 The safe bet seems to be Alki, but if we want to spend our social time in downtown we now need to consider the transportation costs.
 
-```{r, include = F}
-# Difference of proportions test:
-mytable1<-seattle1 %>% filter(cancellation_policy=='strict')%>%
-  group_by(host_neighbourhood) %>% tally()
-mytable2<-seattle1 %>% group_by(host_neighbourhood) %>% tally()
-mytable1
-mytable2
-p1hat= mytable1[[1,2]]/mytable2[[1,2]]
-p2hat= mytable1[[2,2]]/mytable2[[2,2]]
-phatdiff = p1hat - p2hat
-ppooled = (mytable1[[1,2]]+mytable1[[2,2]])/(mytable2[[1,2]]+mytable2[[2,2]])
-stderror = sqrt(ppooled*(1-ppooled)*(1/mytable2[[1,2]]+1/mytable2[[2,2]]))
-tstat = phatdiff/stderror
-2*pnorm(tstat)
-
-seattle1<-seattle %>% select(cancellation_policy, neighbourhood_cleansed)
-
-seattle1<- seattle1 %>% filter( (neighbourhood_cleansed == 'Alki' | 
-                                      neighbourhood_cleansed == 'Belltown'))
-
-ggplot(seattle1, aes(x = neighbourhood_cleansed, fill = cancellation_policy)) + 
-  geom_bar(position = 'fill') + coord_flip() + ylab('Proportion')+ xlab('Neighborhood')+
-  ggtitle('Cancellation Policy in Two Neighborhoods')
-
+```{r, echo = showcode, eval = F}
+#Descriptive statistics: 
 mytable1<-seattle1 %>% filter(cancellation_policy=='strict')%>%
@@
 mytable2<-seattle1 %>% group_by(neighbourhood_cleansed) %>% tally()
-mytable1
-mytable2
-p1hat= mytable1[[1,2]]/mytable2[[1,2]]
-p2hat= mytable1[[2,2]]/mytable2[[2,2]]
+x1<-mytable1[[1,2]]
+x2<-mytable1[[2,2]]
+n1<-mytable2[[1,2]]
+n2<-mytable2[[2,2]]
+p1hat= x1/n1
+p2hat= x2/n2
+
+#Difference of proportions tests:
+
+#Parametric (Z-test)
 phatdiff = p1hat - p2hat
-ppooled = (mytable1[[1,2]]+mytable1[[2,2]])/(mytable2[[1,2]]+mytable2[[2,2]])
-stderror = sqrt(ppooled*(1-ppooled)*(1/mytable2[[1,2]]+1/mytable2[[2,2]]))
+ppooled = (x1+x2)/(n1+n2)
+stderror = sqrt(ppooled*(1-ppooled)*(1/n1+1/n2))
 tstat = phatdiff/stderror
-pvalue = 2*pnorm(tstat)
+pvaue<- 2*pnorm(tstat)
 
-#p-value = 9.214435e-05
+#Nonparametric (Chi-Squared-test)
+prop.test(x = c(x1,x2), n = c(n1,n2))
 
@@
 
-```{r,echo = F, fig.height = 2.5,message = F, warnings = FALSE}
-seattle1<-seattle %>% select(price, beds)
-seattle1<-na.omit(seattle1)
-#ggpairs(airbnb6)
+```{r,echo = showcode, fig.height = 2.5,message = F, warnings = FALSE}
+#Let's 
+# - eliminate all variables except price and # of beds
+# - eliminate missing data (... but worry about what missing data means...)
+seattle1<-seattle %>% 
+  select(price, beds) %>%
+  na.omit()%>%
+  filter(beds<=14)
 
-seattle1<-seattle1 %>%filter(beds<=14)
+#Create a jittered scatterplot which also shows the best fit line: 
+p1<-ggplot(seattle1, aes(x = beds, y = price)) + geom_jitter(shape = 1) + xlim(0,11)+
+  geom_smooth(method = 'lm',se = F) + xlab('# of Beds') + ylab('Price')
 
-p1<-ggplot(seattle1, aes(x = beds, y = price)) + geom_jitter(shape = 1) + xlim(0,11)+
-  #ggtitle('Price versus Number of Beds')#+ 
-  geom_smooth(method = 'lm',se = F)
-
-#p1
-#ggplot(seattle1, aes(x = beds, y = price)) + 
-#  stat_density2d(aes(fill = ..level..), geom="polygon")+
-#  xlim(0.5,11)+ylim(0,1000)
-
+#Create a contour plot to show where data is most dense: 
 p2<-ggplot(seattle1, aes(x = beds, y = price)) + 
-  stat_density2d(na.rm=TRUE) + xlim(0.5,3.5) +ylim(0,250)
-  #geom_smooth(method = 'lm')+
-  #ggtitle('2D Density Contours')
+  stat_density2d(na.rm=TRUE) + xlim(0.5,3.5) +ylim(0,250)+
+  xlab('# of Beds') + ylab('Price')
 
 plot_grid(p1, p2)
+
+#Simple linear regression: 
 m1<-with(lm(price~beds), data = seattle1)
@@
 
-A simple linear regression tells us that the best-fit line for our data is approximately $Price = \$46 + 47\cdot beds$, 
+A simple linear regression tells us that the best-fit line for our data is approximately
+
+\[
+\text{Price  in \$}= \$46 + \frac{\$47}{\text{bed}} \cdot\left( \text{\# of beds}\right), 
+\]
+
 so, I should expect to pay about \$93 for a rental with one bed and \$47 more per additional bed.
-As an additional exploration, you might try find a 95% confidence interval for the true slope (marginal price) of this regression line.
+You might next want to try find a 95% confidence interval for the true slope (marginal price) of this regression line.
 What about a 95% confidence interval for the average price of rentals with 3 beds?
@@
 A good idea for each of the following explorations would be to split your data into a training and a test set so that you can test your predictions on data that your model has not seen.
-As you work on these explorations consider the following questions: Which variables turn out to be the most important?
-The least inportant?
-Are there any variables that amount to just 'noise' in this analysis?
-How reliable do you think your model is?
-Do you think this same model would work in other regions of the world?
-Why or why not?
-Do you think it would be necessary to pre-process that data in any way?
-<!--For example, do you think that it would be necessary to do a principal component analysis on your data first in order to reduce the dimension of the data set?-->  Do you think that the variables should be transformed in any way?
-Do you think any additional features should be included in your data (e.g.
-the square of a feature, the product of two features, etc)?
+
+As you work on these explorations consider the following questions:
+
+  * Which variables turn out to be the most important?  The least important? 
+  * Are there any variables that amount to just 'noise' in this analysis?
+  * How reliable do you think your model is?  
+  * Do you think this same model would work in other regions of the world?  Why or why not? 
+  * Do you think it would be necessary to pre-process that data in any way?
+<!--For example, do you think that it would be necessary to do a principal component analysis on your data first in order to reduce the dimension of the data set?-->
+  * Do you think that the variables should be transformed in any way? 
+  * Do you think any additional features should be included in your data (e.g. the square of a feature, the product of two features, etc)?
 
@@
 
-```{r, echo = F, eval = F}
+```{r, echo = showcode, eval = F}
 seattle1<-seattle %>% select(price, accommodates, beds, bathrooms,
@@
 
-```{r, eval = F, echo = F}
+```{r, eval = F, echo = showcode}
 #================== Use Multiple Logistic Regression =====================
@@
 
-```{r, eval = F, echo = F}
+```{r, eval = F, echo = showcode}
 

### 2017-06-07 ArticleDraft.Rmd
Mathmanda edited beyond the basics, intro and conclusion.  Added a formatted version of the word file

@@
 library(rpart) #classification trees
+library(rpart.plot) #plots of classification trees
+library(car) # marginal model plots
 
@@
 
-Data is seemingly everywhere these days, and is becoming more powerful as we learn how to use it to answer important questions.
+According to 
+Jonathan Rosenberg, adviser to Larry Page and former SVP of products at Google, 
+"Data is the sword of the 21st century, those who weild it well, the samurai."
+The world of data and data analysis is growing in importance, and those with the interest and appropriate skillset are uniquely positioned to solve interesting problems and answer vital questions.
+
 In this article we highlight one freely-available, rich and complex data set which you might use to try out asking and answering data-driven questions. 
-
 What follows are a collection of explorations that you can try out along with us.
@@
 ## Moving Beyond the Basics
+
 In this section we pose more questions and leave the investigations open to you.
@@
 ###Exploration #6:
+
 What variables in this data set do you think would be the most useful in predicting the price of a particular rental?
-Try `accommodates`, `beds`, `bathrooms`, `guests_included`, `review_scores_rating`, and various neighborhoods, and see if you can build a model (maybe a multiple regression, regression tree, or artificial neural network) that is *good* at predicting prices.
+For example, try `accommodates`, `beds`, `bathrooms`, `guests_included`, `review_scores_rating`, and dummy variables for various neighborhoods, and see if you can build a model (maybe a multiple regression, regression tree, or artificial neural network) that is good at predicting prices.
 
@@
 ```{r, echo = showcode, eval = F}
-seattle1<-seattle %>% select(price, accommodates, beds, bathrooms,
+#First, let's keep only the variables we're interested in:
+seattle1<-seattle %>% 
+  select(price, accommodates, beds, bathrooms,
           guests_included,review_scores_rating, neighbourhood_cleansed)
 
-#What are the most popular neighbourhoods? 
-seattle1 %>% group_by(neighbourhood_cleansed) %>% tally() %>% arrange(desc(n))
+# Let's look at how these variables relate to each other
+# by creating a scatterplot matrix:
+ggpairs(seattle1[,1:6])
+#It looks like price is correlated with accomodates, beds, and baths ...
+# but these are also correlated with each other!
 
-nbd_list<-c('Broadway', 'Wallingford', 'Belltown')
-seattle1<-seattle1 %>% filter(neighbourhood_cleansed %in% nbd_list)
+# Does price seem to be related to neighbourhood? 
+seattle1 %>% group_by(neighbourhood_cleansed) %>%
+  summarise(mean = mean(price), median = median(price), n = n())%>%
+  arrange(desc(n))
 
-#Let's look at how these variables relate to each other: 
-ggpairs(seattle1, cardinality_threshold = 90)
+# Belltown seems to cost more than other neighborhoods.
+# University District seems to cost less than other neighborhoods.
+# Let's create dummy variables for Belltown and University District.
 
-#It looks like price is correlated with accomodates, beds, and baths ... but these are also correlated with each other! Does it seem to be related to neighbourhood?
-
-seattle1 %>% group_by(neighbourhood_cleansed) %>% summarise(mean = mean(price), median = median(price))
-#Belltown seems to cost more than the other two.  Let's create a dummy variable for Belltown.
-
-seattle1<- seattle1 %>% mutate(BT=ifelse(neighbourhood_cleansed=='Belltown',1,0))
+seattle1<- seattle1 %>% mutate(
+  BT=ifelse(neighbourhood_cleansed=='Belltown',1,0),
+  UD=ifelse(neighbourhood_cleansed=='University District',1,0))
 
@@
 
-m1<-lm(price~ accommodates+beds+bathrooms +guests_included+review_scores_rating+BT, data = seattle1 )
+m1<-lm(price~ accommodates+beds+bathrooms+
+         guests_included+review_scores_rating+BT+UD, data = seattle1 )
 summary(m1)
 
-#At first glance it appears that we can explain about 43% of the variation in price using these variables, and the ones that seem to contribute the most are 'accomodates', 'bathrooms, 'guests_included', and 'BT' (perhaps, in that order).
-But...
-does it seem weird to you that 'beds' is not in this list?
-Can you explain why it's not?
-There are many ways to decide which variables to include (like stepwise regression, or contextual knowledge of the problem).
-Let's naively just take the ones I mentioned above:
+#At first glance it appears that we can explain about 47% of the variation
+#in price using these variables, and all variables seem to contribute to 
+#price except 'beds'.
 
-seattle2<-seattle1 %>% select(price, accommodates, bathrooms, guests_included, BT)
+#Does it seem weird to you that 'beds' doesn't seem to contribute significantly? 
+#Can you explain why it's not?
+
+#There are many ways to decide which variables to include 
+# (like stepwise regression, or contextual knowledge of the problem).  
+# Let's naively just take the ones I mentioned above:
+
+seattle2<-seattle1 %>% select(-beds)
 seattle2<-na.omit(seattle2)
-m2<-lm(price~ accommodates+bathrooms +guests_included+BT, data = seattle2 )
+m2<-lm(price~ accommodates+bathrooms+guests_included+
+         review_scores_rating+BT+UD, data = seattle2 )
 summary(m2)
 stres<-rstandard(m2)
-#Interestingly, we can now explain something like 47% of the variation in price, suggesting some of the variables we dropped were maybe acting like red herrings!
-If we choose to accept this model (which, by the way, we shouldn't -- at least not until we assess its validity!), a practical description of the model would be:
+#Interestingly, we can still explain about 47% of the variation in price, 
+#suggesting that eliminating 'beds' doesn't cost us any predictive power.
+# If we choose to accept this model 
+# (which, by the way, we shouldn't -- at least not until we assess its validity!), 
+# a practical description of the model would be:
 
-#An (empty) rental costs $0. 
-# - For every person the rental accomodates, add $25.65 to the price
-# - For every bathroom in the rental, add $35.69 to the price
-# - For each guest included, add $7.27 o the rental price
-# - If the rental is in BellTown, add $19 to the price
+# - For every person the rental accomodates, add $21.20 to the price
+# - For every bathroom in the rental, add $35.15 to the price
+# - For each guest included, add $6.52 o the rental price
+# - For each point in the rating, add $.68 to the rental price
+# - If the rental is in BellTown, add $30.47 to the price
+# - If the rental is in University District, subtract $14.19 from the price
 
-#Assess validity of model: Do the residuals appear to be normally distributed? 
-p1<-ggplot(seattle2, aes(x = accommodates, y = rstandard(m2))) + geom_point(shape = 1)
-p2<-ggplot(seattle2, aes(x = bathrooms, y = rstandard(m2))) + geom_point(shape = 1)
-p3<-ggplot(seattle2, aes(x = guests_included, y = rstandard(m2))) + geom_point(shape = 1)
+#What is the *practical* significance of the coefficients explained above?  
+#For example, it seems like 'accommodates' and 'bathrooms' add a significant 
+# amount of money to the price.  On the other hand, 'review_scores_rating' 
+# *seems* statistically significant, adding 68 cents to the price of a rental 
+# above $100 seems irrelevant (even if it is true).
+
+#If you were going to open an Airbnb in Seattle, 
+# which of the variables above would you consider, in order to maximize your profits?
+
+#If you are interested in assessing the validity of our model, ask: 
+# Do the residuals appear to be normally distributed? 
+p1<-ggplot(seattle2, aes(x = accommodates, y = rstandard(m2))) + geom_point(shape = 1)+ xlab('# Accommodated') + ylab('St. Residuals')
+p2<-ggplot(seattle2, aes(x = bathrooms, y = rstandard(m2))) + geom_point(shape = 1)+
+   xlab('# Bathrooms') + ylab('St. Residuals')
+p3<-ggplot(seattle2, aes(x = guests_included, y = rstandard(m2))) + 
+  geom_point(shape = 1)+ xlab('# Guests Included') + ylab('St. Residuals')
 p4<-ggplot(seattle2, aes(x = lm.influence(m2)$hat, y = rstandard(m2))) + 
@@
   geom_hline(yintercept = -4, color = 'red')+ 
-  geom_hline(yintercept = 4, color = 'red')
+  geom_hline(yintercept = 4, color = 'red')+ xlab('Influence Score') + ylab('St. Residuals')
 plot_grid(p1,p2,p3,p4)
-ggplot(seattle2, aes(x = fitted(m2), y = price)) + geom_point(shape = 1)
+ggplot(seattle2, aes(x = fitted(m2), y = rstandard(m2))) + geom_point(shape = 1)+
+  xlab('Fitted Values') + ylab('St. Residuals')
 
-#While there is no recognizable nonlinear shape in these residual plots, we do have a number of 'outlier + leverage' points that could be skewing things for us.
-Also, the variation of residuals appears to be growing as accomodates/bathroom get larger.
-So, this model has some problems.
+#While there is no recognizable nonlinear shape in these residual plots, 
+# we do have a number of 'outlier + leverage' points that are problematic.  
+# Also, the variation of residuals appears to be growing as things get larger. 
+# So, this model is not without its problems.
 
@@
 
-#The following code produces a regression tree for this problem:
-t<-tree(price~ accommodates+beds+bathrooms +guests_included+review_scores_rating+BT, data = seattle1 )
+#Produces a regression tree:
+t<-tree(price~ accommodates+beds+bathrooms +guests_included+review_scores_rating+BT+UD, data = seattle1 )
 t
 plot(t)
-text(t) # *********** this line errors **************
+text(t)
 
 #It appears that the most important variable in the data is 'accomodates'.  
-#If you just want to split the data into two groups, you should look to see if the renatl accomodates 8 or more people.
-If so, the average price would be $390, if not the average price would be $125.
-#For the rentals which accomodate less than 8 people, the next break occurs depending on if he rental accomodates four or more people (average price $163.10) or not (average price $102.20).
-#The next break occurs in the rentals that accommodate more than 8 people: rentals in Belltown (average price $539) or not (average price $342.70).
+#If you just want to split the data into two groups, you should look to
+# see if the rental accomodates 5 or more people.  
+#     If so, the average price would be $223, 
+#     If not the average price would be $102.
+
+#For the rentals which accomodate less than 5 people, 
+# the next break occurs depending on 
+#    if he rental accomodates three or four people (average price $128.10) 
+#    or not (average price $85.51).
+
+#The next break occurs in the rentals that accommodate 5 or more people: 
+#     rentals with two or fewer bathrooms (average price $188) 
+#     or more than two (average price $326).
 
@@
 #1 - Can you interpret the meaning behind all of the breaks? 
-#2 - Does the regression tree change your mind about which variables (in which cases) are practically significant? 
-#3 - Which model do you think is better?
+#2 - How many 'breaks' in the tree would you consider necessary, 
+#     before you might be 'overfitting' the data? Why?
+#3 - Does this regression tree change your mind about which variables (in which cases) are practically significant? 
+#4 - Which model we've produced so far do you think is better for predicting price?
 
@@
 
+# First, we consider only the variables we care about: 
 seattle1<-seattle %>% select(room_type, price, accommodates, beds, bathrooms,
-                            guests_included,review_scores_rating, neighbourhood_cleansed)
+                            guests_included,review_scores_rating,
+                            neighbourhood_cleansed)
+
+#For simplicity, let's eliminate the Shared rooms, as they are irrelevant here
 seattle1<- seattle1 %>% filter(room_type != 'Shared room')
@@
 
-#Which neighborhoods have more Private rentals? 
-seattle1 %>% group_by(neighbourhood_cleansed) %>% summarize(p = mean(Private))%>%
-  arrange(p)
-
 #Suppose we only use price to predict whether a rental is a private room (instead of an entire house)
-
 m1<-glm(Home~ price, family = binomial, data = seattle1 )
 c<-coefficients(m1)
-
+#We create the logistic function that has been estimated: 
 f<-function(x){1/(1 + exp(-c[[1]] -c[[2]]*x))}
 
-seattlebinned<-seattle1 %>% mutate(pricebin = cut(price, breaks = 20*0:100, labels = 20*0.5:99.5))
+#In order to create a visualization of what we've just done, we're going to bin our data into buckets of observations that have similar prices, and compare their proportion of 'entire home' rentals':
+seattlebinned<-seattle1 %>% 
+  mutate(pricebin = cut(price, breaks = 20*0:100, labels = 20*0.5:99.5))
 seattleb<-seattlebinned %>% group_by(pricebin) %>% summarise(p = mean(Home))
@@
 # Let's try adding more variables: 
-
 seattle2<-na.omit(seattle1)
@@
 
-m3<-glm(Home~ accommodates+bathrooms +review_scores_rating + price, family = binomial, data = seattle2 )
+#Somewhat arbitrarily, I've decided to keep accomodates, bathrooms, and price: 
+m3<-glm(Home~ accommodates+bathrooms  + price, family = binomial, data = seattle2 )
 summary(m3)
 
+#How effectively does this predict 'entire home's? 
 seattle2<- seattle2 %>% mutate(Predict = ifelse(fitted(m3)>.5, 1, 0))
 classError(seattle2$Home,seattle2$Predict )
-#New error rate: 13%.  Not that much better?
+#New error rate: 13.8%.  Not that much better?
 
@@
 
-t<-rpart(Home~ accommodates+beds+bathrooms +guests_included+review_scores_rating + price, 
-         data = seattle2 )
+#Now, let's produce a classification tree for this question: 
+t<-rpart(Home~ accommodates+beds+bathrooms +guests_included+
+           review_scores_rating + price, data = seattle2 )
 t
-plot(t, compress = TRUE)
-text(t, use.n = TRUE)
+rpart.plot(t, compress = TRUE)
 
-#Fix plot and add interpretation
+#1 - Can you interpret the meaning behind all of the breaks in this tree? 
+#2 - How many 'breaks' in the tree would you consider necessary, 
+#     before you might be 'overfitting' the data? Why?
+#3 - Does this classification tree change your mind about which variables 
+#    (and in which cases) are practically significant? 
+#4 - Which model we've produced so far do you think is better for 
+#    predicting Homes vs. private rooms?
 
@@
 ```{r, eval = F, echo = showcode}
-
+#As usual, let's start by isolating the variables we care about: 
 seattle1<-seattle %>% select(room_type, price, accommodates, beds, bathrooms,
@@
                             neighbourhood_cleansed,latitude, longitude)
-#Which nbds should we pick
-seattle1 %>% group_by(neighbourhood_cleansed) %>% tally() %>% arrange(desc(n))
-#Howabout: 
-nbd_list<-c('Broadway', 'Belltown', 'Wallingford', 'University District', 'Minor')
+
+#We've decided to use the following 5 neighbourhoods:  
+nbd_list<-c('Broadway', 'Belltown', 'University District', 'Minor','Fremont')
+#Let's eliminate all rentals that aren't in these neighborhoods: 
 seattle1<-seattle1 %>% filter(neighbourhood_cleansed %in% nbd_list)
@@
 
-seattle1 %>% tbl_df()
-
+#Now we create a new data set with a dummy variable for 'entire home' and 
+# elminating non-numeric variables
 clusters<-seattle1 %>%
   mutate(Home = ifelse(room_type == 'Entire home/apt',1,0)) %>%
-  select(-neighbourhood_cleansed,-room_type)
+  select(-neighbourhood_cleansed,-room_type)%>%
+  na.omit()
 
-clusters<-na.omit(clusters)
-km<-kmeans(cbind(clusters[,1:8]),5)
+#K-means is a way to determining clusters in data by trying to minimize
+# 'within-cluster-sum-of-squares'
+#What if we try to detect just 2 clusters here 
+km<-kmeans(cbind(clusters[,1],clusters[,7:8]),3)
 clusters<-clusters %>% mutate(Predict = km$cluster)
-
 ggplot(clusters, aes(x = longitude, y = latitude, color = as.factor(Predict))) + 
@@
 
-#Still need to play around with variables.  Or, just give up and use latitude and longitude only...
+#As you play around with the code above you may notice a few of the following things: # - Each time we xecute the code above we get potentially different clusters, as this method depends on randomly chosen starting locations
+# - Some number of clusters work well, if we guess at too many or too few, we get bad results
+# - Latitude and Longitude get almost ignored when any other variable is tossed into the model.
+Is this because the variability in lat/long is so small compared to other variables?
+If so, can you think of a way to compat that?
+
+#Let's try using only lat/long, and trying to decide what the optimal number of clusters is: 
+wcc<-NULL
+for(i in 2:10){
+  wcc<-c(wcc,sum(kmeans(clusters[,7:8],i)$withinss))	
+}
+plot(seq(2,10),wcc,type="b",pch=1,xlab="# of Clusters",
+     ylab="Within Sum--Squares")
+#In the 'elbow plot' above, we look for places where the slope changes drastically
+
+#Suppose you choose 4 clusters: 
+km<-kmeans(clusters[,7:8],4)
+clusters<-clusters %>% mutate(Predict = km$cluster)
+ggplot(clusters, aes(x = longitude, y = latitude, color = as.factor(Predict))) + 
+  geom_point()
+
+#How could you improve our clustering model? 
+#Can you think of a way to not rely on latitude and longitude?
 
@@
 ##Conclusions
-The Insideairbnb data set is robust enough that anyone with statistical training, no matter the sophistication, can ask meaningful and challenging questions.
-In recent times the field of data science has become a successful and popular way to analyze data sets of this type.
-If you want to learn more about exploring and using data for analysis and predictions there are starter courses on the web (e.g., Coursera and DataCamp) and many universities and colleges around the world are implementing Data Science programs.
-Most importantly, as you may have found from the last three exercises, the level of mathematical sophistication associated with data analysis can be quite high, so if you are a student reading this article and you find the ideas interesting then we recommend taking courses in statistics, computer science and computational mathematics.
 
-There are many data sets like Insiderairbnb available for free on the internet.
-For example, the University of California, Irnive, hosts a collection of machine learning data sets that are at least as rich and interesting (archive.ics.uci.edu/ml/).
+<!--The Insideairbnb data set is robust enough that anyone with statistical training, no matter the sophistication, can ask meaningful and challenging questions.-->  Recently, the field of data science has become a successful and popular way to analyze data like the one presented in this article.
+If you want to learn more about this field, there are starter courses on the web (e.g., Coursera and DataCamp) and many universities and colleges around the world are implementing data science programs.
+As you may have discovered in the last three exercises, the level of mathematical sophistication associated with data analysis can be quite high, so if you find the data-driven problems interesting, then we recommend taking more courses in statistics, computer science and computational mathematics!
+For, as  Jennifer Pahlka, Founder and Executive Director for Code for America has said: "[o]ur ability to do great things with data will make a real difference in every aspect of our lives."
+
+Many data sets like the one we've considered here are available for free online.  
+For example, some of our favorite places to find interesting (and real) data are
+
+  * data.gov
+  * kaggle.com
+  * archive.ics.uci.edu/ml
+  * Quandl.com
+  * gapminder.org
+  * flowingdata.com
+
+<!--For example, the University of California, Irnive, hosts a collection of machine learning data sets that are at least as rich and interesting (archive.ics.uci.edu/ml/).
 Other sites to look at when seeking data sets include data.gov, kaggle.com, quandl.com, gapminder.org, flowingdata.com, and many others.
-The world of data and data analysis is growing in importance socially and mathematicians and statisticians are uniquely positioned with their training to approach these questions with proper skills and mindsets.
+-->

### 2017-06-07 ArticleDraft.Rmd
A few heading problems fixed
Fixed tree plots, elbow plot, and minor tweak to intro.

@@
 library(GGally) # scatterplot matrices
-library(tree) # regression trees
-library(rpart) #classification trees
+library(rpart) #regression and classification trees
 library(rpart.plot) #plots of classification trees
@@
 According to 
-Jonathan Rosenberg, adviser to Larry Page and former SVP of products at Google, 
+Jonathan Rosenberg, <!--adviser to Larry Page and--> former SVP of products at Google, 
 "Data is the sword of the 21st century, those who weild it well, the samurai."
@@
 
-###Exploration #6:
+### Exploration #6:
 
@@
 #Produces a regression tree:
-t<-tree(price~ accommodates+beds+bathrooms +guests_included+review_scores_rating+BT+UD, data = seattle1 )
+t<-rpart(price~ accommodates+beds+bathrooms +guests_included+review_scores_rating+BT+UD, data = seattle1 )
 t
-plot(t)
-text(t)
+rpart.plot(t)
 
@@
 # see if the rental accomodates 5 or more people.  
-#     If so, the average price would be $223, 
-#     If not the average price would be $102.
+#     If so, the average price would be $227, 
+#     If not the average price would be $104.
 
@@
 # the next break occurs depending on 
-#    if he rental accomodates three or four people (average price $128.10) 
-#    or not (average price $85.51).
+#    if the rental accomodates four people (average price $140) 
+#    or not (average price $91).
 
 #The next break occurs in the rentals that accommodate 5 or more people: 
-#     rentals with two or fewer bathrooms (average price $188) 
-#     or more than two (average price $326).
+#     rentals with two or fewer bathrooms (average price $192) 
+#     or more than two (average price $324).
 
@@
 #Let's try using only lat/long, and trying to decide what the optimal number of clusters is: 
-wcc<-NULL
+wss<-NULL
 for(i in 2:10){
-  wcc<-c(wcc,sum(kmeans(clusters[,7:8],i)$withinss))	
+  wss<-c(wss,sum(kmeans(clusters[,7:8],i)$withinss))
                }
-plot(seq(2,10),wcc,type="b",pch=1,xlab="# of Clusters",
-     ylab="Within Sum--Squares")
-#In the 'elbow plot' above, we look for places where the slope changes drastically
+df<-data.frame(x = 2:10, y = wss)
+ggplot(df, aes(x = x, y = y)) + geom_line() + geom_point(shape = 7)+
+  xlab('# of Clusters') + ylab('Within Sum of Squares') + ggtitle('Elbow Plot')
+#In the 'elbow plot' above, we look for places where the slope changes drastically (elbows!)
 
 #Suppose you choose 4 clusters: 
-km<-kmeans(clusters[,7:8],4)
+km<-kmeans(clusters[,7:8],5)
 clusters<-clusters %>% mutate(Predict = km$cluster)
@@
 
-##Conclusions
+## Conclusions
 

### 2017-06-07 ArticleDraft.Rmd
June 7 12:46 Sullivan edits

@@
 According to 
-Jonathan Rosenberg, <!--adviser to Larry Page and--> former SVP of products at Google, 
-"Data is the sword of the 21st century, those who weild it well, the samurai."
+Jonathan Rosenberg, <!--adviser to Larry Page and--> former Senior Vice President of products at Google, 
+"[d]ata is the sword of the 21st century, those who wield it well, the samurai."
 The world of data and data analysis is growing in importance, and those with the interest and appropriate skillset are uniquely positioned to solve interesting problems and answer vital questions.
@@
 In this article we highlight one freely-available, rich and complex data set which you might use to try out asking and answering data-driven questions. 
-What follows are a collection of explorations that you can try out along with us.
+<!--What follows are -->We propose a collection of explorations that you can try out along with us.
 After each exploration we’ll give some of our own thoughts, discussion, and visualization.
@@
 Go to insideairbnb.com now and find a data set for the city of your choice.
-Spend a few minutes exploring the data set and propose several questions.
 When you press “Get the Data” on insideairbnb.com and find your city you will see a link “see data visually here”.
-Spend some time exploring their visual aids.
+Spend some time exploring their visual aids, exploring the data set and proposing several questions that can be answered from the data.
 
@@
 ## Initial Exploratory Data Analysis
-<!--As a way to motivate statistical thinking and exploration on these large Airbnb data sets--> Let’s explore some questions related to your particular city (These explorations are meant to increase in difficulty as you work through them).
+<!--As a way to motivate statistical thinking and exploration on these large Airbnb data sets--> Let’s explore some questions related to your particular city<!-- (these explorations are meant to increase in difficulty as you work through them)-->.
 
@@
 You’re trying to budget your travel money.
-Give a *pracical* estimate for the daily prices of an Airbnb rentals in a particular neighborhood.
+Give a *pracical* estimate for the daily prices of Airbnb rentals in a particular neighborhood.
 <!-- In what range of daily prices would you expect the average daily price for a private room at an Airbnb in a particular neighborhood to land?
@@
 Let's filter the data to explore the prices of rentals from the Alki beach area.
-We'll start with some basic descriptive statistics: the average rental price there is $172 but the standard deviation is $97!
-The question in this exploration is best answered with a range of prices, and, based on the rather large standard deviation, the estimate will have a rather large range as well.
+We'll start with some basic descriptive statistics: the average rental price in the Alki neighborhood is $172 but the standard deviation is $97!
+The question in this exploration is best answered with a range of prices, and, based on the <!--rather--> large standard deviation, the estimate will likely have a rather large range<!-- as well-->.
 If this data were normally distributed we would expect *most* of the rentals (~68% of them) to be withing one standard deviation of the mean: between $75 and $269.
@@
 Do you wonder if hosts with cleaner rentals charge more?
-Here is a more specific question:  is there a significant difference between the daily price of the *cleanest* rentals verus the *least clean* rentals?
+More specifically, <!--Here is a more specific question:  -->is there a significant difference between the daily price of the *cleanest* rentals verus the *least clean* rentals?
 
 **Discussion:** 
-The first order of business in this exploration is to decide what *cleanest and *least clean* mean to us.
+The first order of business in this exploration is to decide what *cleanest* and *least clean* mean to us.
 The cleanliness rating scale goes from 0 to 10, but we shouldn't assume that cleanliness ratings are evenly distributed among these numbers, or even that the numbers 0-10 represent a linear progression of cleanliness.
@@
 --> We assume that every dot we see represents one rental, but there may be places in this scatterplot where many dots all landed on top of each other.
-
 One option is to add a ‘jitter’ to our graphic, so that we can see all (or, at least, more) of our points, which will help us get a sense about where our clusters are.
@@
 The visualization above shows us the distribution of cancellation policies in the two neighborhoods, and a statistical test on the difference of the  proportions of *strict* policies in each neighborhood gives us a p-value much less than .01, and we  conclude that there is evidence to suggest that rentals in Belltown have a much stricter cancellation policy than those in Alki.
-The safe bet seems to be Alki, but if we want to spend our social time in downtown we now need to consider the transportation costs.
+The safe bet seems to be Alki, but if we want to spend our social time in downtown, near Belltown, we now need to consider the transportation costs.
 
@@
 tstat = phatdiff/stderror
-pvaue<- 2*pnorm(tstat)
+pvalue<- 2*pnorm(tstat)
 
@@
 ```{r,echo = showcode, fig.height = 2.5,message = F, warnings = FALSE}
-#Let's 
+# Let's 
 # - eliminate all variables except price and # of beds
@@
 ## Moving Beyond the Basics 
-
 In this section we pose more questions and leave the investigations open to you.
@@
 What variables in this data set do you think would be the most useful in predicting the price of a particular rental?
-For example, try `accommodates`, `beds`, `bathrooms`, `guests_included`, `review_scores_rating`, and dummy variables for various neighborhoods, and see if you can build a model (maybe a multiple regression, regression tree, or artificial neural network) that is good at predicting prices.
+For example, try `accommodates`, `beds`, `bathrooms`, `guests_included`, `review_scores_rating`, and <!--dummy variables for -->various neighborhoods, and see if you can build a model (maybe a multiple regression, regression tree, or artificial neural network) that is good at predicting prices.
 
@@
 If you want to learn more about this field, there are starter courses on the web (e.g., Coursera and DataCamp) and many universities and colleges around the world are implementing data science programs.
-As you may have discovered in the last three exercises, the level of mathematical sophistication associated with data analysis can be quite high, so if you find the data-driven problems interesting, then we recommend taking more courses in statistics, computer science and computational mathematics!
-For, as  Jennifer Pahlka, Founder and Executive Director for Code for America has said: "[o]ur ability to do great things with data will make a real difference in every aspect of our lives."
+As you may have discovered in the last three exercises, the level of mathematical sophistication associated with data science can be quite high, so if you find the data-driven problems interesting, then we recommend taking more courses in statistics, computer science and computational mathematics!
+As Jennifer Pahlka, Founder and Executive Director for Code for America, has said: "[o]ur ability to do great things with data will make a real difference in every aspect of our lives."
 
-Many data sets like the one we've considered here are available for free online.  
+Many data sets like the one we've considered in this article are available for free online.  
 For example, some of our favorite places to find interesting (and real) data are
@@
 
+This work was funded by a grant from the the W.M. Keck Foundation.
 <!--For example, the University of California, Irnive, hosts a collection of machine learning data sets that are at least as rich and interesting (archive.ics.uci.edu/ml/).

### 2017-06-07 ArticleDraft.Rmd
Two commas

@@
 When you press “Get the Data” on insideairbnb.com and find your city you will see a link “see data visually here”.
-Spend some time exploring their visual aids, exploring the data set and proposing several questions that can be answered from the data.
+Spend some time exploring their visual aids, exploring the data set, and proposing several questions that can be answered from the data.
 
@@
 <!--The Insideairbnb data set is robust enough that anyone with statistical training, no matter the sophistication, can ask meaningful and challenging questions.-->  Recently, the field of data science has become a successful and popular way to analyze data like the one presented in this article.
-If you want to learn more about this field, there are starter courses on the web (e.g., Coursera and DataCamp) and many universities and colleges around the world are implementing data science programs.
+If you want to learn more about this field, there are starter courses on the web (e.g., Coursera and DataCamp), and many universities and colleges around the world are implementing data science programs.
 As you may have discovered in the last three exercises, the level of mathematical sophistication associated with data science can be quite high, so if you find the data-driven problems interesting, then we recommend taking more courses in statistics, computer science and computational mathematics!

### 2017-06-07 ArticleDraft.Rmd
Changed 1st violin plot color

@@
 
-```{r, echo = showcode,fig.height = 2,fig.width = 5}
+```{r, echo = showcode,fig.height = 2.5,fig.width = 5}
 #First we filter our data so that only includes the neighbourhood we care about: 
@@
 #Create a boxplot + violin plot to see what prices happen most: 
-ggplot(seattle1, aes(x = 'Alki', y = price)) + geom_violin(fill = 'cyan')+
-  geom_boxplot(width = .3, fill = 'Lightblue')+coord_flip() + xlab('') + ylab('Price')+
+ggplot(seattle1, aes(x = 'Alki', y = price)) + geom_violin(fill = 'mediumorchid3')+
+  geom_boxplot(width = .3, fill = 'mediumorchid1')+coord_flip() + xlab('') + ylab('Price')+
   ggtitle('Distribution of Prices in the Alki Neighborhood')

### 2017-06-15 ArticleDraft.Rmd
Sullivan commits June 15, 2:22pm after Dave's initial comments

@@
 #Create a boxplot + violin plot to see what prices happen most: 
-ggplot(seattle1, aes(x = 'Alki', y = price)) + geom_violin(fill = 'mediumorchid3')+
+ggplot(seattle1, aes(x = '', y = price)) + geom_violin(fill = 'mediumorchid3')+
   geom_boxplot(width = .3, fill = 'mediumorchid1')+coord_flip() + xlab('') + ylab('Price')+
@@
 Having learned from our last exploration, this time let's look at a visualization of the data first.
-How about a scatterplot of cleanliness rating versus price?
+<!--How about a scatterplot of cleanliness rating versus price?-->  How about we start with a bar graph of the counts of the cleanliness scores.
 
@@
 #Make a scatterplot of cleanliness rating versus price: 
-ggplot(seattle1, aes(x = review_scores_cleanliness, y = price)) + geom_point()+
-  ggtitle('Scatterplot') + xlab('Cleanliness Score') + ylab('Price')
+# ggplot(seattle1, aes(x = review_scores_cleanliness, y = price)) + geom_point()+
+#   ggtitle('Scatterplot') + xlab('Cleanliness Score') + ylab('Price')
+
+ggplot(seattle1, aes(x= review_scores_cleanliness))+
+  ggtitle('Bar Graph of Cleanliness Ratings') +
+  geom_bar(width=0.9, fill="steelblue") + 
+  xlab('Cleanliness Score')
 ```
 
+It appears that the number of ratings drops off drastically below a cleanliness score of 8.
+Hence, we conjecture that the ratings between 0 and 7 represent the people that are truly unhappy with the cleanliness of the rental.
+<!--
 One problem with this graphic is that the dots we've plotted are likely hiding the very information we want!
-<!--Some of the dots might represent only one observation, while some may have many rental observations which happen to have the same cleanliness review score and price as many others.
---> We assume that every dot we see represents one rental, but there may be places in this scatterplot where many dots all landed on top of each other.
+We assume that every dot we see represents one rental, but there may be places in this scatterplot where many dots all landed on top of each other.-->
+To include the price into the discussion we now consider a scatter plot of cleanliness score versus the price.
+An immediate concern, however, is that many of the points will undoubtedly overlap and make the plot difficult to read.
 One option is to add a ‘jitter’ to our graphic, so that we can see all (or, at least, more) of our points, which will help us get a sense about where our clusters are.
@@
 
-The jittered scatterplot suggests that 7 might be a good *cut-off* value for separating clean and unclean rentals.
-Notice that the sample sizes are wildly different: 80 rentals with lower cleanliness ratings and 3,165 with higher ratings.
+<!--The jittered scatterplot suggests that 7 might be a good *cut-off* value for separating clean and unclean rentals.
+-->Notice that the sample sizes are wildly different: 80 rentals with lower cleanliness ratings and 3,165 with higher ratings.
 <!--Perhaps people are just too nice in their ratings or perhaps the Airbnb properties in Seattle are clean!--> It *looks* like the rentals rated higher for cleanliness get better prices, perhaps with a few outliers.

### 2017-06-15 Exploration_2.R

@@ -1,0 +1,31 @@
+library(ggplot2) # graphics
+library(dplyr) # data wrangling
+library(cowplot) #plot grids
+library(knitr) # fancy tables
+library(GGally) # scatterplot matrices
+library(rpart) #regression and classification trees
+library(rpart.plot) #plots of classification trees
+library(car) # marginal model plots 
+seattle<-read.csv('Airbnb_Seattle.csv')
+currency_to_numeric <- function(x){
+  # Convert currencies to numeric i.e. strip dollar signs and commas
+  x <- gsub('\\$','', as.character(x))
+  x <- gsub('\\,','', as.character(x))
+  x <- as.numeric(x)
+  return(x)
+}
+seattle<-seattle %>% mutate(price = currency_to_numeric(price))
+showcode<-F
+
+#First we filter our data so that only includes the neighbourhood we care about: 
+seattle1<-seattle %>% filter(neighbourhood_cleansed == 'Alki')
+
+#Calculate the mean and standard deviation:
+m = mean(seattle1$price)
+s = sd(seattle1$price)
+
+#Create a boxplot + violin plot to see what prices happen most: 
+ggplot(seattle1, aes(x = '', y = price)) + geom_violin(fill = 'mediumorchid3')+
+  geom_boxplot(width = .3, fill = 'mediumorchid1')+coord_flip() + xlab('') + ylab('Price')+
+  ggtitle('Distribution of Prices in the Alki Neighborhood')
+

### 2017-06-15 Exploration_3.R

@@ -1,0 +1,49 @@
+library(ggplot2) # graphics
+library(dplyr) # data wrangling
+library(cowplot) #plot grids
+library(knitr) # fancy tables
+library(GGally) # scatterplot matrices
+library(rpart) #regression and classification trees
+library(rpart.plot) #plots of classification trees
+library(car) # marginal model plots 
+seattle<-read.csv('Airbnb_Seattle.csv')
+currency_to_numeric <- function(x){
+  # Convert currencies to numeric i.e. strip dollar signs and commas
+  x <- gsub('\\$','', as.character(x))
+  x <- gsub('\\,','', as.character(x))
+  x <- as.numeric(x)
+  return(x)
+}
+seattle<-seattle %>% mutate(price = currency_to_numeric(price))
+showcode<-F
+
+#For simplicity, let's eliminate all variables except cleanliness score and price
+# and eliminate any missing data
+# .... though .... we should consider what missing data might mean about a rental ...
+seattle1<- seattle %>% 
+  select(review_scores_cleanliness, price)%>%
+  filter(review_scores_cleanliness != 'N/A')
+
+# Make a bar graph of the cleanliness ratings
+ggplot(seattle1, aes(x= review_scores_cleanliness))+
+  ggtitle('Bar Graph of Cleanliness Ratings') +
+  geom_bar(width=0.9, fill="steelblue") + 
+  xlab('Cleanliness Score')
+
+# We make a jittered scatterplot, and indicate a potential cut-off value for 
+# cleanest vs least clean: 
+ggplot(seattle1, aes(x = review_scores_cleanliness, y = price)) +
+  geom_jitter(shape = 1) + 
+  geom_segment(y = 0, yend = 1000, x = 7.5, xend = 7.5 , color = 'red')+
+  ggtitle('Jittered Scatterplot')+ xlab('Cleanliness Score')+ ylab('Price')
+
+#Let's create a new variable that separates the clean from the unclean!
+seattle1 <- seattle1 %>% mutate(HiLo = ifelse(review_scores_cleanliness>=8, 'High', 'Low'))
+
+#Now we make side by side violin and boxplots, so we can compare prices 
+#of the two groups: 
+ggplot(seattle1, aes(x = HiLo, y = price, fill = HiLo))+
+  geom_violin()+geom_boxplot( width = .4)+coord_flip()+
+  theme(legend.position = "none")+
+  scale_y_log10() + 
+  xlab('Cleanliness Rating') + ylab('Price')+ggtitle('Price on a Log Scale')

### 2017-06-15 Exploration_4.R

@@ -1,0 +1,54 @@
+library(ggplot2) # graphics
+library(dplyr) # data wrangling
+library(cowplot) #plot grids
+library(knitr) # fancy tables
+library(GGally) # scatterplot matrices
+library(rpart) #regression and classification trees
+library(rpart.plot) #plots of classification trees
+library(car) # marginal model plots 
+seattle<-read.csv('Airbnb_Seattle.csv')
+currency_to_numeric <- function(x){
+  # Convert currencies to numeric i.e. strip dollar signs and commas
+  x <- gsub('\\$','', as.character(x))
+  x <- gsub('\\,','', as.character(x))
+  x <- as.numeric(x)
+  return(x)
+}
+seattle<-seattle %>% mutate(price = currency_to_numeric(price))
+showcode<-F
+
+#Let's eliminate all variables except neighbourhood and cancellation policies,
+# and filter out the irrelevant neighbourhoods.
+seattle1<-seattle %>%
+  select(cancellation_policy,neighbourhood_cleansed)%>%
+  filter( (neighbourhood_cleansed == 'Alki' |  neighbourhood_cleansed == 'Belltown'))
+
+#Create a visualization showing the different distributions of cancellation policies
+ggplot(seattle1, aes(x = neighbourhood_cleansed, fill = cancellation_policy)) + 
+  geom_bar(position = 'fill') + coord_flip() + ylab('Proportion')+ xlab('Neighborhood')+
+  ggtitle('Cancellation Policy in Two Neighborhoods')
+
+#Descriptive statistics: 
+mytable1<-seattle1 %>% filter(cancellation_policy=='strict')%>%
+  group_by(neighbourhood_cleansed) %>% tally()
+mytable2<-seattle1 %>% group_by(neighbourhood_cleansed) %>% tally()
+x1<-mytable1[[1,2]]
+x2<-mytable1[[2,2]]
+n1<-mytable2[[1,2]]
+n2<-mytable2[[2,2]]
+p1hat= x1/n1
+p2hat= x2/n2
+
+
+#Difference of proportions tests:
+
+#Parametric (Z-test)
+phatdiff = p1hat - p2hat
+ppooled = (x1+x2)/(n1+n2)
+stderror = sqrt(ppooled*(1-ppooled)*(1/n1+1/n2))
+tstat = phatdiff/stderror
+pvalue<- 2*pnorm(tstat)
+
+
+#Nonparametric (Chi-Squared-test)
+prop.test(x = c(x1,x2), n = c(n1,n2))

### 2017-06-15 Exploration_5.R

@@ -1,0 +1,42 @@
+library(ggplot2) # graphics
+library(dplyr) # data wrangling
+library(cowplot) #plot grids
+library(knitr) # fancy tables
+library(GGally) # scatterplot matrices
+library(rpart) #regression and classification trees
+library(rpart.plot) #plots of classification trees
+library(car) # marginal model plots 
+seattle<-read.csv('Airbnb_Seattle.csv')
+currency_to_numeric <- function(x){
+  # Convert currencies to numeric i.e. strip dollar signs and commas
+  x <- gsub('\\$','', as.character(x))
+  x <- gsub('\\,','', as.character(x))
+  x <- as.numeric(x)
+  return(x)
+}
+seattle<-seattle %>% mutate(price = currency_to_numeric(price))
+showcode<-F
+
+# Let's 
+# - eliminate all variables except price and # of beds
+# - eliminate missing data (... but worry about what missing data means...)
+seattle1<-seattle %>% 
+  select(price, beds) %>%
+  na.omit()%>%
+  filter(beds<=14)
+
+#Create a jittered scatterplot which also shows the best fit line: 
+p1<-ggplot(seattle1, aes(x = beds, y = price)) + geom_jitter(shape = 1) + xlim(0,11)+
+  geom_smooth(method = 'lm',se = F) + xlab('# of Beds') + ylab('Price')
+
+#Create a contour plot to show where data is most dense: 
+p2<-ggplot(seattle1, aes(x = beds, y = price)) + 
+  stat_density2d(na.rm=TRUE) + xlim(0.5,3.5) +ylim(0,250)+
+  xlab('# of Beds') + ylab('Price')
+
+plot_grid(p1, p2)
+
+#Simple linear regression: 
+m1<-with(lm(price~beds), data = seattle1)
+s<-summary(m1)
+#kable(s$coefficients)

### 2017-06-15 Exploration_6.R

@@ -1,0 +1,139 @@
+library(ggplot2) # graphics
+library(dplyr) # data wrangling
+library(cowplot) #plot grids
+library(knitr) # fancy tables
+library(GGally) # scatterplot matrices
+library(rpart) #regression and classification trees
+library(rpart.plot) #plots of classification trees
+library(car) # marginal model plots 
+seattle<-read.csv('Airbnb_Seattle.csv')
+currency_to_numeric <- function(x){
+  # Convert currencies to numeric i.e. strip dollar signs and commas
+  x <- gsub('\\$','', as.character(x))
+  x <- gsub('\\,','', as.character(x))
+  x <- as.numeric(x)
+  return(x)
+}
+seattle<-seattle %>% mutate(price = currency_to_numeric(price))
+showcode<-F
+
+
+#First, let's keep only the variables we're interested in:
+seattle1<-seattle %>% 
+  select(price, accommodates, beds, bathrooms,
+         guests_included,review_scores_rating, neighbourhood_cleansed)
+
+# Let's look at how these variables relate to each other
+# by creating a scatterplot matrix:
+ggpairs(seattle1[,1:6])
+#It looks like price is correlated with accomodates, beds, and baths ...
+# but these are also correlated with each other! 
+
+# Does price seem to be related to neighbourhood? 
+seattle1 %>% group_by(neighbourhood_cleansed) %>%
+  summarise(mean = mean(price), median = median(price), n = n())%>%
+  arrange(desc(n))
+
+# Belltown seems to cost more than other neighborhoods.
+# University District seems to cost less than other neighborhoods.
+# Let's create dummy variables for Belltown and University District. 
+
+seattle1<- seattle1 %>% mutate(
+  BT=ifelse(neighbourhood_cleansed=='Belltown',1,0),
+  UD=ifelse(neighbourhood_cleansed=='University District',1,0))
+
+#================== Use Multiple Regression =====================
+
+m1<-lm(price~ accommodates+beds+bathrooms+
+         guests_included+review_scores_rating+BT+UD, data = seattle1 )
+summary(m1)
+
+#At first glance it appears that we can explain about 47% of the variation
+#in price using these variables, and all variables seem to contribute to 
+#price except 'beds'.  
+
+#Does it seem weird to you that 'beds' doesn't seem to contribute significantly? 
+#Can you explain why it's not? 
+
+#There are many ways to decide which variables to include 
+# (like stepwise regression, or contextual knowledge of the problem).  
[…]

### 2017-06-15 Exploration_7.R

@@ -1,0 +1,86 @@
+library(ggplot2) # graphics
+library(dplyr) # data wrangling
+library(cowplot) #plot grids
+library(knitr) # fancy tables
+library(GGally) # scatterplot matrices
+library(rpart) #regression and classification trees
+library(rpart.plot) #plots of classification trees
+library(car) # marginal model plots 
+seattle<-read.csv('Airbnb_Seattle.csv')
+currency_to_numeric <- function(x){
+  # Convert currencies to numeric i.e. strip dollar signs and commas
+  x <- gsub('\\$','', as.character(x))
+  x <- gsub('\\,','', as.character(x))
+  x <- as.numeric(x)
+  return(x)
+}
+seattle<-seattle %>% mutate(price = currency_to_numeric(price))
+showcode<-F
+
+
+#================== Use Multiple Logistic Regression =====================
+
+# First, we consider only the variables we care about: 
+seattle1<-seattle %>% select(room_type, price, accommodates, beds, bathrooms,
+                             guests_included,review_scores_rating,
+                             neighbourhood_cleansed)
+
+#For simplicity, let's eliminate the Shared rooms, as they are irrelevant here
+seattle1<- seattle1 %>% filter(room_type != 'Shared room')
+seattle1<- seattle1 %>% mutate(Home = ifelse(room_type == 'Private room', 0, 1))
+
+
+#Suppose we only use price to predict whether a rental is a private room (instead of an entire house)
+m1<-glm(Home~ price, family = binomial, data = seattle1 )
+c<-coefficients(m1)
+#We create the logistic function that has been estimated: 
+f<-function(x){1/(1 + exp(-c[[1]] -c[[2]]*x))}
+
+#In order to create a visualization of what we've just done, we're going to bin our data into buckets of observations that have similar prices, and compare their proportion of 'entire home' rentals':
+seattlebinned<-seattle1 %>% 
+  mutate(pricebin = cut(price, breaks = 20*0:100, labels = 20*0.5:99.5))
+seattleb<-seattlebinned %>% group_by(pricebin) %>% summarise(p = mean(Home))
+ggplot(seattleb, aes(x = currency_to_numeric(pricebin), y = p)) + geom_point()+
+  stat_function(fun = f, color = 'blue') + xlab('Price')+xlim(0,500)
+#The graphic deomonstrates that an increase of price is linked to an increased likelihood that the rental is an entire home. 
+
+
+summary(m1)
[…]

### 2017-06-15 Exploration_8.R

@@ -1,0 +1,68 @@
+library(ggplot2) # graphics
+library(dplyr) # data wrangling
+library(cowplot) #plot grids
+library(knitr) # fancy tables
+library(GGally) # scatterplot matrices
+library(rpart) #regression and classification trees
+library(rpart.plot) #plots of classification trees
+library(car) # marginal model plots 
+seattle<-read.csv('Airbnb_Seattle.csv')
+currency_to_numeric <- function(x){
+  # Convert currencies to numeric i.e. strip dollar signs and commas
+  x <- gsub('\\$','', as.character(x))
+  x <- gsub('\\,','', as.character(x))
+  x <- as.numeric(x)
+  return(x)
+}
+seattle<-seattle %>% mutate(price = currency_to_numeric(price))
+showcode<-F
+
+#As usual, let's start by isolating the variables we care about: 
+seattle1<-seattle %>% select(room_type, price, accommodates, beds, bathrooms,
+                             guests_included ,review_scores_rating,
+                             neighbourhood_cleansed,latitude, longitude)
+
+#We've decided to use the following 5 neighbourhoods:  
+nbd_list<-c('Broadway', 'Belltown', 'University District', 'Minor','Fremont')
+#Let's eliminate all rentals that aren't in these neighborhoods: 
+seattle1<-seattle1 %>% filter(neighbourhood_cleansed %in% nbd_list)
+ggplot(seattle1, aes(x = longitude, y = latitude, color = neighbourhood_cleansed)) + 
+  geom_point()
+
+#Now we create a new data set with a dummy variable for 'entire home' and 
+# elminating non-numeric variables
+clusters<-seattle1 %>%
+  mutate(Home = ifelse(room_type == 'Entire home/apt',1,0)) %>%
+  select(-neighbourhood_cleansed,-room_type)%>%
+  na.omit()
+
+#K-means is a way to determining clusters in data by trying to minimize
+# 'within-cluster-sum-of-squares'
+#What if we try to detect just 2 clusters here 
+km<-kmeans(cbind(clusters[,1],clusters[,7:8]),3)
+clusters<-clusters %>% mutate(Predict = km$cluster)
+ggplot(clusters, aes(x = longitude, y = latitude, color = as.factor(Predict))) + 
+  geom_point()
+
+#As you play around with the code above you may notice a few of the following things: # - Each time we xecute the code above we get potentially different clusters, as this method depends on randomly chosen starting locations
[…]
